---
title: "MVPA - HPC unsmoothed"
author: "Catherine Walsh"
date: "8/30/2020"
output:
  html_document:
    toc: true 
    toc_float: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Another potentially interesting question we can try to answer is how much face representation we see across the task. In order to do so, we've trained a linear SVM classifier within subjects on the data from the smoothed FFA localizer to classify signal into faces, objects and scrambles. We can then apply that classifier to various facets of our data. For each of these analyses, we will look at the probability of the classifier predicting a face. If the classifier does indeed predict a face, we score that TR with a "1", otherwise, it gets a "0", meaning chance becomes 1/3 = .33. 

First, we will apply it to each TR of individual trials. Trials are split into 4 bins based on accuracy and load, and averaged over those measures to create a single time course for each category. The classifier was also applied to each TR of a "template" for each condition. In this analysis, all trials in a given condition were averaged to create a prototypical example for the category. The classifier was then applied to those averages. 

We can then look at the probability of classification across subjects. First, we look at it across all subjects, but then we can look at it across our working memory capacity groups. 

Finally, we will relate these neural measures to behavior, both averaged over time and for each TR. 

```{r import packages, data etc}

library(reshape2)
library(tidyverse)
library(patchwork)

load('data/behav.RData')
load('data/split_groups_info.RData')
load('data/DFR_split_groups_info.RData')

source("helper_fxns/split_into_groups.R")
source('helper_fxns/prep_trial_levels_for_plot.R')
source("helper_fxns/split_trial_type.R")

se <- function(x) {
  sd(x,na.rm=TRUE)/sqrt(length(x[!is.na(x)])) 
}

```

```{r load in data}
#classifier information
clf_acc <- read.csv('data/MVPA/HPC_unsmoothed/clf_acc.csv', header=FALSE)
best_c <- read.csv('data/MVPA/HPC_unsmoothed/best_C.csv', header=FALSE)
trial_acc <- read.csv("data/MVPA/HPC_unsmoothed/all_suj_acc.csv", header = FALSE)
colnames(trial_acc) <- c('low correct', 'low incorrect', 'high correct', 'high incorrect')

# averaages from template 
averages_from_template <- list(high_correct = read.csv('data/MVPA/HPC_unsmoothed/all_suj_high_correct_avg.csv',header=FALSE), 
                               high_incorrect = read.csv('data/MVPA/HPC_unsmoothed/all_suj_high_incorrect_avg.csv',header=FALSE), 
                               low_correct = read.csv('data/MVPA/HPC_unsmoothed/all_suj_low_correct_avg.csv',header=FALSE), 
                               low_incorrect = read.csv('data/MVPA/HPC_unsmoothed/all_suj_low_incorrect_avg.csv',header=FALSE))

# only want to look at subjects who have at least 4 low load incorrect trials for those analyses 
min_low_incorrect <- which(trial_acc$`low incorrect` < 4)
averages_from_template[["low_incorrect"]][min_low_incorrect, 1:14] <- NA

averages_from_template[["high_load_correct_diff"]] <- averages_from_template[["high_correct"]][,1:14] - averages_from_template[["high_incorrect"]][,1:14]
averages_from_template[["low_load_correct_diff"]] <- averages_from_template[["low_correct"]][,1:14] - averages_from_template[["low_incorrect"]][,1:14]

# averages from individual trials
individual_trial_averages_probs <- list(
  high_correct = read.csv('data/MVPA/HPC_unsmoothed/all_suj_high_correct_indiv_avg_probs.csv',header=FALSE),
  high_incorrect = read.csv('data/MVPA/HPC_unsmoothed/all_suj_high_incorrect_indiv_avg_probs.csv',header=FALSE),
  low_correct = read.csv('data/MVPA/HPC_unsmoothed/all_suj_low_correct_indiv_avg_probs.csv',header=FALSE),
  low_incorrect = read.csv('data/MVPA/HPC_unsmoothed/all_suj_low_incorrect_indiv_avg_probs.csv',header=FALSE)) 

individual_trial_averages_probs[["low_incorrect"]][min_low_incorrect, 1:14] <- NA

individual_trial_averages_probs[["high_load_correct_diff"]] <- individual_trial_averages_probs[["high_correct"]][,1:14] - individual_trial_averages_probs[["high_incorrect"]][,1:14]
individual_trial_averages_probs[["low_load_correct_diff"]] <- individual_trial_averages_probs[["low_correct"]][,1:14] - individual_trial_averages_probs[["low_incorrect"]][,1:14]

# averages from individual trials
individual_trial_averages_preds <- list(
  high_correct = read.csv('data/MVPA/HPC_unsmoothed/all_suj_high_correct_indiv_avg_preds.csv',header=FALSE),
  high_incorrect = read.csv('data/MVPA/HPC_unsmoothed/all_suj_high_incorrect_indiv_avg_preds.csv',header=FALSE),
  low_correct = read.csv('data/MVPA/HPC_unsmoothed/all_suj_low_correct_indiv_avg_preds.csv',header=FALSE),
  low_incorrect = read.csv('data/MVPA/HPC_unsmoothed/all_suj_low_incorrect_indiv_avg_preds.csv',header=FALSE)) 

individual_trial_averages_preds[["low_incorrect"]][min_low_incorrect, 1:14] <- NA

individual_trial_averages_preds[["high_load_correct_diff"]] <- individual_trial_averages_preds[["high_correct"]][,1:14] - individual_trial_averages_preds[["high_incorrect"]][,1:14]

individual_trial_averages_preds[["low_load_correct_diff"]] <- individual_trial_averages_preds[["low_correct"]][,1:14] - individual_trial_averages_preds[["low_incorrect"]][,1:14]


averages_from_template2 <- list()
indiv_probs <- list()
indiv_preds <- list()

for (i in seq.int(1,6)){
  averages_from_template2[[names(averages_from_template)[i]]] <- averages_from_template[[i]][c(1:9,11:170),]
  indiv_preds[[names(averages_from_template)[i]]] <- individual_trial_averages_preds[[i]][c(1:9,11:170),]
  indiv_probs[[names(averages_from_template)[i]]] <- individual_trial_averages_probs[[i]][c(1:9,11:170),]
  for (ii in seq.int(1,14)){
    
    averages_from_template2[[i]][is.nan(averages_from_template2[[i]][,ii]),ii] <- NA
    indiv_probs[[i]][is.nan(indiv_probs[[i]][,ii]),ii] <- NA
    indiv_preds[[i]][is.nan(indiv_preds[[i]][,ii]),ii] <- NA
    
  }
  averages_from_template2[[i]]$PTID <- constructs_fMRI$PTID[c(1:9,11:170)]
  indiv_probs[[i]]$PTID <- constructs_fMRI$PTID[c(1:9,11:170)]
  indiv_preds[[i]]$PTID <- constructs_fMRI$PTID[c(1:9,11:170)]
  
}

averages_from_template <- averages_from_template2
individual_trial_averages_preds <- indiv_preds
individual_trial_averages_probs <- indiv_probs

rm(averages_from_template2)
rm(indiv_preds)
rm(indiv_probs)

save(list=c("clf_acc", "best_c", "averages_from_template", "individual_trial_averages_probs","individual_trial_averages_preds"), file = "data/MVPA_HPC_unsmoothed.RData")

```

# Probability of classifying faces 

On average, we were able to classify faces with 42.2% accuracy (statistically significantly different from chance = 0.33). The classifier was trained on data from an independent FFA localizer. Data was extracted from the bilateral hippocampus. From that mask, the top 100 voxels based on the faces vs objects contrast in the overall subject GLM were selected as features for the classifier. The data used to train the classifier were shifted by 4.5 seconds to account for the hemodynamic delay. 

A linear SVM classifer was used; the localizer task was split into 6 blocks of stimuli. These blocks were used in a pre-defined split for cross validation, where one block of each stimulus type was held out as a test set. Data were normalized within the training and test sets separately. Within this training set, another cross validation process was repeated to tune the cost of the model over the values [0.01, 0.1, 1, 10]. The best value of the cost function was used for each cross validation to score the classifier on the test set. The best classifer was also used to predict face presence at each TR during the DFR task. 

We can see that there are a number of subjects for whom the classifier works below chance - we'll remove those from the analysis

```{r calculate classifier average}

clf_acc$average <- rowMeans(clf_acc, na.rm = TRUE)
t.test(clf_acc$average,mu=0.33)

ggplot(data = clf_acc, aes(x = average))+ 
  geom_histogram()+
  geom_vline(aes(xintercept=0.33), linetype="dotted")+
  theme_classic()+
  xlab("Average classifier accuracy")


```

```{r remove subs with below chance classification}

below_chance_subjs <- which(clf_acc$average < 0.33)

for (trial_type in seq.int(1,6)){
  averages_from_template[[trial_type]][below_chance_subjs,] <- NA
  individual_trial_averages_preds[[trial_type]][below_chance_subjs,] <- NA
  individual_trial_averages_probs[[trial_type]][below_chance_subjs,] <- NA
}

```


```{r average over all subjects}

template_preds_melt <- prep_trial_levels_for_plot(averages_from_template)
individual_trial_probs_melt <- prep_trial_levels_for_plot(individual_trial_averages_probs)
individual_trial_preds_melt <- prep_trial_levels_for_plot(individual_trial_averages_preds)

```

## All subjects

The shape of the time course is different here than it was for the fusiform region - here, we're well below chance for encoding, but start to see a significant probability during delay (starting around TR 8) and the probe. 

### From individual trials 

Here, we're seeing a similiar pattern to the fusform, where we see peaks of decoding accuracy around the encoding period and then probe period. However, unlike the fusiform, we're also seeing above chance accuracy for all trial types during the delay period. We also see that during encoding, high load trials (regardless of accuracy) show a higher probability of having a face decoded than low load trials. There are no differences between trial types, however, during probe.  

```{r plot individual trial avgs for all subjects}

ggplot(data=individual_trial_probs_melt %>% filter(level %in% c("high_correct", "high_incorrect", "low_correct", "low_incorrect")),aes(x=TR,y=value))+
  geom_line(aes(color=level))+
  geom_line(aes(x=TR,y=0.33),color="black",linetype="dotted")+
  geom_ribbon(aes(x=TR,ymin=se_min,ymax=se_max,fill=level),alpha=0.2)+
  scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
  ylab("Probability of classifier predicting a face")+
  theme_classic()


```

```{r delay period diff from chance}

t.test(individual_trial_averages_probs[["high_correct"]]$V8,mu=0.33)
t.test(individual_trial_averages_probs[["high_incorrect"]]$V8,mu=0.33)
t.test(individual_trial_averages_probs[["low_correct"]]$V8,mu=0.33)
t.test(individual_trial_averages_probs[["low_incorrect"]]$V8,mu=0.33)


```

```{r compare indiv encoding prob}

encoding_level_avg <- data.frame(high = rowMeans(cbind(individual_trial_averages_probs[["high_correct"]]$V6, individual_trial_averages_probs[["high_incorrect"]]$V6), na.rm=TRUE), low = rowMeans(cbind(individual_trial_averages_probs[["low_correct"]]$V6, individual_trial_averages_probs[["low_incorrect"]]$V6),na.rm=TRUE))

t.test(encoding_level_avg$high,encoding_level_avg$low,paired=TRUE)

encoding_acc_avg <- data.frame(correct = rowMeans(cbind(individual_trial_averages_probs[["high_correct"]]$V6, individual_trial_averages_probs[["low_correct"]]$V6), na.rm=TRUE), incorrect = rowMeans(cbind(individual_trial_averages_probs[["low_incorrect"]]$V6, individual_trial_averages_probs[["high_incorrect"]]$V6),na.rm=TRUE))

t.test(encoding_acc_avg$correct,encoding_acc_avg$incorrect,paired=TRUE)


```

```{r probe indiv anova}

probe_data_indiv <- data.frame(high_correct=individual_trial_averages_probs[["high_correct"]]$V11, 
                               high_incorrect = individual_trial_averages_probs[["high_incorrect"]]$V11, 
                               low_correct = individual_trial_averages_probs[["low_correct"]]$V11,
                               low_incorrect = individual_trial_averages_probs[["low_incorrect"]]$V11)
probe_data_indiv <- melt(probe_data_indiv)

probe.aov <- aov(value ~ variable, data = probe_data_indiv)
summary(probe.aov)
TukeyHSD(probe.aov)


```

It seems like there's really not much difference between correct and incorrect trials in the hippocampus. 

```{r plot differences between correctness for all subjects}

ggplot(data=individual_trial_probs_melt %>% filter(level %in% c("low_load_correct_diff","high_load_correct_diff")),aes(x=TR,y=value))+
  geom_line(aes(x=TR,y=0), linetype="dotted")+
  geom_line(aes(color=level))+
  geom_ribbon(aes(x=TR,ymin=se_min,ymax=se_max,fill=level),alpha=0.2)+
  scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
  ylab("Correct - Incorrect Diff in Probability of Classifying Faces")+
  theme_classic()

```

### From templates

In the templates, we see a similar structure as in the individual trials with peaks around encoding and probe, though there is below chance decoding during delay period. There are no differences between trial types during probe. 

```{r plot template average over all subjects}

ggplot(data=template_preds_melt%>% filter(level %in% c("high_correct", "high_incorrect", "low_correct", "low_incorrect")),aes(x=TR,y=value))+
  geom_line(aes(color=level))+
  geom_line(aes(x=TR,y=0.33),color="black",linetype="dotted")+
  geom_ribbon(aes(x=TR,ymin=se_min,ymax=se_max,fill=level),alpha=0.2)+
  scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
  ylab("Probability of classifier predicting a face")+
  theme_classic()

```

```{r test differences in accuracy}

acc_data_probe <- data.frame(correct = rowMeans(cbind(averages_from_template[["high_correct"]]$V10,averages_from_template[["low_correct"]]$V10)), 
                             incorrect = rowMeans(cbind(averages_from_template[["high_incorrect"]]$V10, averages_from_template[["low_incorrect"]]$V10)))
t.test(acc_data_probe$correct,acc_data_probe$incorrect, paired=TRUE)

acc_data_late_probe <- data.frame(correct = rowMeans(cbind(averages_from_template[["high_correct"]]$V11,averages_from_template[["low_correct"]]$V11)), 
                                  incorrect = rowMeans(cbind(averages_from_template[["high_incorrect"]]$V11, averages_from_template[["low_incorrect"]]$V11)))
t.test(acc_data_late_probe$correct,acc_data_late_probe$incorrect, paired=TRUE)

```


```{r probe template anova}

probe_data_template <- data.frame(high_correct=averages_from_template[["high_correct"]]$V11, 
                                  high_incorrect = averages_from_template[["high_incorrect"]]$V11, 
                                  low_correct = averages_from_template[["low_correct"]]$V11,
                                  low_incorrect = averages_from_template[["low_incorrect"]]$V11)
probe_data_template <- melt(probe_data_template)

probe.aov <- aov(value ~ variable, data = probe_data_template)
summary(probe.aov)
TukeyHSD(probe.aov)

```

Unlike in the other regions, there is no difference in the overall probability of predicting a face from the template vs individual trials. 

```{r compare template to indiv trials}

compare_across_temp_indiv <- data.frame(template = rowMeans(cbind(averages_from_template[["high_correct"]]$V10,
                                                                  averages_from_template[["high_incorrect"]]$V10,
                                                                  averages_from_template[["low_correct"]]$V10)),
                                        indiv = rowMeans(cbind(individual_trial_averages_probs[["high_correct"]]$V10,
                                                               individual_trial_averages_probs[["high_incorrect"]]$V10,
                                                               individual_trial_averages_probs[["low_correct"]]$V10)))

wilcox.test(compare_across_temp_indiv$template, compare_across_temp_indiv$indiv,paired=TRUE)

```

Similar to before, there aren't any differences between correct and incorrect trials from the template. 

```{r plot differences between correctness for template}

ggplot(data=template_preds_melt %>% filter(level %in% c("low_load_correct_diff","high_load_correct_diff")),aes(x=TR,y=value))+
  geom_line(aes(color=level))+
  geom_line(aes(x=TR,y=0), linetype="dotted")+
  geom_ribbon(aes(x=TR,ymin=se_min,ymax=se_max,fill=level),alpha=0.2)+
  scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
  ylab("Correct - Incorrect Diff in Probability of Classifying Faces")+
  theme_classic()

```

```{r test correctness diffs}

encoding_correct_diff_high <- data.frame(correct=averages_from_template[["high_correct"]]$V6, incorrect=averages_from_template[["high_incorrect"]]$V6)

probe_correct_diff_high <- data.frame(correct=averages_from_template[["high_correct"]]$V11, incorrect=averages_from_template[["high_incorrect"]]$V11)

t.test(encoding_correct_diff_high$correct, encoding_correct_diff_high$incorrect, paired=TRUE)
t.test(probe_correct_diff_high$correct, probe_correct_diff_high$incorrect, paired=TRUE)


```


## By Working Memory Capacity Groups 

```{r split into groups}

split_template <- split_trial_type(averages_from_template,WM_groups)
split_indiv_probs <- split_trial_type(individual_trial_averages_probs, WM_groups)
split_indiv_preds <- split_trial_type(individual_trial_averages_preds, WM_groups)

```

### From Indiv Trials  

In high load incorrect trials, we see that medium capacity subjects show greater face classification than both low and high capacity subjects during encoding, and greater than low capacity subjects during low load correct trials.   

```{r split group indiv prob plots}

indiv_avgs <- list()

for (i in seq.int(1,4)){
  indiv_avgs[[i]] <- ggplot(data = split_indiv_probs[["avgs"]][[i]][["all"]])+
    geom_line(aes(x=TR,y=mean,color=group))+
    geom_ribbon(aes(x=TR,ymin=se_min,ymax=se_max,fill=group),alpha=0.2)+
    geom_line(aes(x=TR,y=0.33),color="black",linetype="dotted")+
    scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
    ggtitle(names(split_indiv_probs[["avgs"]])[i])+
    ylab("Probability")+
    theme_classic()
  
}

(indiv_avgs[[1]] + indiv_avgs[[2]]) / (indiv_avgs[[3]] + indiv_avgs[[4]])+
  plot_layout(guides = "collect")+
  plot_annotation(title="Probability of classifier predicting a face from individual trials")

```

```{r anova between groups indiv}

print("encoding")
for (trial_type in seq.int(1,4)){ 
  print(names(split_indiv_probs[["all_data"]])[trial_type])
  temp.aov <- aov(split_indiv_probs[["all_data"]][[trial_type]][["all"]][,6] ~ split_indiv_probs[["all_data"]][[trial_type]][["all"]][,16])
  print(summary(temp.aov))
  print(TukeyHSD(temp.aov))
}

```

### From templates 

There are no group differences at encoding from the template. 

```{r split group template prob plots}

template_avgs <- list()

for (i in seq.int(1,4)){
  template_avgs[[i]] <- ggplot(data = split_template[["avgs"]][[i]][["all"]])+
    geom_line(aes(x=TR,y=mean,color=group))+
    geom_ribbon(aes(x=TR,ymin=se_min,ymax=se_max,fill=group),alpha=0.2)+
    geom_line(aes(x=TR,y=0.33),color="black",linetype="dotted")+
    scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
    ggtitle(names(split_template[["avgs"]])[i])+
    ylab("Probability")+
    theme_classic()
  
}

(template_avgs[[1]] + template_avgs[[2]]) / (template_avgs[[3]] + template_avgs[[4]])+
  plot_layout(guides = "collect")+
  plot_annotation(title="Probability of classifier predicting a face from trial templates")

```

```{r anova between groups template}

for (trial_type in seq.int(1,4)){ 
  print(names(split_template[["all_data"]])[trial_type])
  temp.aov <- aov(split_template[["all_data"]][[trial_type]][["all"]][,6] ~ split_template[["all_data"]][[trial_type]][["all"]][,16])
  print(summary(temp.aov))
  print(TukeyHSD(temp.aov))
}

```

# Correlation with Behavior 

## Individual Trials

### Averaged over time

If we look averaged over time, we see a significant positive correlation with omnibus span and the difference between classification at corect and incorrect low load trials. We also see significant negative correlation between high load accuacy and decoding at low load incorrect trials, and between BPRS and classification at high load incorrect trials, and a positive cprrelation with the differnce between correct and incorrect at high load trials. 

```{r make plots to correlate indiv over time}

indiv_avg_over_time <- data.frame(high_correct = rowMeans(individual_trial_averages_probs[["high_correct"]][,1:14]),
                                  high_incorrect = rowMeans(individual_trial_averages_probs[["high_incorrect"]][,1:14]),
                                  low_correct = rowMeans(individual_trial_averages_probs[["low_correct"]][,1:14]),
                                  low_incorrect = rowMeans(individual_trial_averages_probs[["low_incorrect"]][,1:14],na.rm=TRUE), 
                                  high_load_diff_correct = rowMeans(individual_trial_averages_probs[["high_load_correct_diff"]][,1:14]),
                                  low_load_diff_correct = rowMeans(individual_trial_averages_probs[["low_load_correct_diff"]][,1:14]))

indiv_avg_over_time[is.na(indiv_avg_over_time)] <- NA 
indiv_avg_over_time <- data.frame(indiv_avg_over_time, omnibus_span = constructs_fMRI$omnibus_span_no_DFR_MRI[c(1:9,11:170)], PTID = constructs_fMRI$PTID[c(1:9,11:170)])
indiv_avg_over_time <- merge(indiv_avg_over_time, p200_data[,c("PTID","BPRS_TOT","XDFR_MRI_ACC_L3", "XDFR_MRI_ACC_L1")],by="PTID")


plot_list <- list()

for (i in seq.int(1,6)){
  plot_data <- indiv_avg_over_time[,c(i+1,8:11)]
  colnames(plot_data)[1] <- "prob"
  plot_list[["omnibus"]][[i]] <- ggplot(data = plot_data,aes(y=prob,x=omnibus_span))+
    geom_point()+
    stat_smooth(method="lm")+
    xlab("Omnibus Span")+
    ggtitle(colnames(indiv_avg_over_time)[i+1])+
    theme_classic()
  
  plot_list[["DFR_Acc"]][[i]] <- ggplot(data = plot_data,aes(y=prob,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    xlab("DFR High Load Acc")+
    ggtitle(colnames(indiv_avg_over_time)[i+1])+
    theme_classic()
  
  plot_list[["BPRS"]][[i]] <- ggplot(data = plot_data,aes(y=prob,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    xlab("BPRS")+
    ggtitle(colnames(indiv_avg_over_time)[i+1])+
    theme_classic()
  
}

(plot_list[["omnibus"]][[1]] + plot_list[["omnibus"]][[2]]) /
  (plot_list[["omnibus"]][[3]] + plot_list[["omnibus"]][[4]]) + 
  plot_annotation(title="Correlation of face probability and Omnibus Span")

(plot_list[["omnibus"]][[5]] + plot_list[["omnibus"]][[6]])+
  plot_annotation(title="Correlation of difference in face probability across correctness and Omnibus Span")

(plot_list[["DFR_Acc"]][[1]] + plot_list[["DFR_Acc"]][[2]]) /
  (plot_list[["DFR_Acc"]][[3]] + plot_list[["DFR_Acc"]][[4]]) + 
  plot_annotation(title="Correlation of face probability and DFR High Load Accuracy")

(plot_list[["DFR_Acc"]][[5]] + plot_list[["DFR_Acc"]][[6]])+
  plot_annotation(title="Correlation of difference in face probability across correctness and DFR High Load Accuracy")

(plot_list[["BPRS"]][[1]] + plot_list[["BPRS"]][[2]]) /
  (plot_list[["BPRS"]][[3]] + plot_list[["BPRS"]][[4]]) + 
  plot_annotation(title="Correlation of face probability and BPRS")
(plot_list[["BPRS"]][[5]] + plot_list[["BPRS"]][[6]])+
  plot_annotation(title="Correlation of difference in face probability across correctness and BPRS")

cor.test(indiv_avg_over_time$low_incorrect, indiv_avg_over_time$omnibus_span)
cor.test(indiv_avg_over_time$low_load_diff_correct, indiv_avg_over_time$omnibus_span)
cor.test(indiv_avg_over_time$low_incorrect, indiv_avg_over_time$XDFR_MRI_ACC_L3)
cor.test(indiv_avg_over_time$low_load_diff_correct, indiv_avg_over_time$XDFR_MRI_ACC_L3)

cor.test(indiv_avg_over_time$high_incorrect, indiv_avg_over_time$BPRS_TOT)
cor.test(indiv_avg_over_time$high_load_diff_correct, indiv_avg_over_time$BPRS_TOT)
cor.test(indiv_avg_over_time$low_load_diff_correct, indiv_avg_over_time$BPRS_TOT)



```

### All subjects

#### Across time 

If we look at the patterns over time, we can see that BPRS tends to be negatively related to classification during encoding and probe periods. There is most correlation with accuracy during the encoding period. Span generally has a low correlation with classification probability. 

Next step is to pull out some of these correlations and see if they're significant. 

```{r make indiv correlations with behav across time for all subj}

data_to_plot <- merge(constructs_fMRI,p200_data,by="PTID")
data_to_plot <- merge(data_to_plot,p200_clinical_zscores,by="PTID")

data_to_plot <- data_to_plot[c(1:9,11:170),c(1,7,14,15,41,42)]
data_to_plot$ACC_LE <- data_to_plot$XDFR_MRI_ACC_L3 - data_to_plot$XDFR_MRI_ACC_L1

corr_to_behav_plots <- list()

for (i in seq.int(1,6)){
  measure_by_time <- data.frame(matrix(nrow=4,ncol=14))
  
  for (measure in seq.int(2,5)){
    for (TR in seq.int(1,14)){
      measure_by_time[measure-1,TR] <- cor(data_to_plot[,measure],individual_trial_averages_probs[[i]][,TR],use = "pairwise.complete.obs")
    }
  }
  
  measure_by_time <- data.frame(t(measure_by_time))
  measure_by_time$TR <- seq.int(1,14)
  
  colnames(measure_by_time)[1:4] <- colnames(data_to_plot)[2:5]
  
  melted_measure_by_time <- melt(measure_by_time,id.vars="TR")
  
  corr_to_behav_plots[[names(individual_trial_averages_probs)[i]]] <- ggplot(data=melted_measure_by_time,aes(x=TR,y=value))+
    geom_line(aes(color=variable))+
    scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
    ggtitle(names(individual_trial_averages_probs)[i])+
    theme_classic()
  
}

```

```{r print TR indiv correlation all subj plots}

(corr_to_behav_plots[[1]] + corr_to_behav_plots[[2]]) / (corr_to_behav_plots[[3]] + corr_to_behav_plots[[4]])+
  plot_layout(guides="collect")+
  plot_annotation(title = "Correlation between face classification and behavioral measures")

(corr_to_behav_plots[[5]] + corr_to_behav_plots[[6]])+
  plot_layout(guides="collect")+
  plot_annotation(title = "Correlation between difference across correctness in face classification and behavioral measures")

```

```{r pull out specfic time points from indiv correlation}

plot_list <- list()

for (trial_type in seq.int(1,6)){ 
  temp_plot_data <- merge(p200_data, individual_trial_averages_probs[[trial_type]],by="PTID")
  temp_plot_data <- merge(temp_plot_data,constructs_fMRI,by="PTID")
  
  plot_list[["omnibus"]][["cue"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V6,x=omnibus_span_no_DFR_MRI))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  plot_list[["omnibus"]][["delay"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V8,x=omnibus_span_no_DFR_MRI))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  plot_list[["omnibus"]][["probe"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V11,x=omnibus_span_no_DFR_MRI))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  # Acc
  
  plot_list[["L3_Acc"]][["cue"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V6,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  plot_list[["L3_Acc"]][["delay"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V8,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  plot_list[["L3_Acc"]][["probe"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V11,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  # BPRS  
  plot_list[["BPRS"]][["cue"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V6,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  plot_list[["BPRS"]][["delay"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V8,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  plot_list[["BPRS"]][["probe"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V11,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(individual_trial_averages_probs)[trial_type])+
    theme_classic()
  
  
}


```

#### Encoding 

There is a significant positive relationship between omnibus span and the difference in decoding probability in correct vs incorrect low load trials. 

```{r plot specific time points from indiv - encoding }

(plot_list[["omnibus"]][["cue"]][[1]] + plot_list[["omnibus"]][["cue"]][[2]]) /  
  (plot_list[["omnibus"]][["cue"]][[3]] + plot_list[["omnibus"]][["cue"]][[4]]) +
  plot_annotation(title = "Omnibus vs Classification at Cue Period")

(plot_list[["omnibus"]][["cue"]][[5]] + plot_list[["omnibus"]][["cue"]][[6]])  +
  plot_annotation(title = "Omnibus vs Classification at Cue Period")

(plot_list[["L3_Acc"]][["cue"]][[1]] + plot_list[["L3_Acc"]][["cue"]][[2]]) /  
  (plot_list[["L3_Acc"]][["cue"]][[3]] + plot_list[["L3_Acc"]][["cue"]][[4]]) +
  plot_annotation(title = "L3_Acc vs Classification at Cue Period")

(plot_list[["L3_Acc"]][["cue"]][[5]] + plot_list[["L3_Acc"]][["cue"]][[6]])  +
  plot_annotation(title = "L3_Acc vs Classification at Cue Period")

(plot_list[["BPRS"]][["cue"]][[1]] + plot_list[["BPRS"]][["cue"]][[2]]) /  
  (plot_list[["BPRS"]][["cue"]][[3]] + plot_list[["BPRS"]][["cue"]][[4]]) +
  plot_annotation(title = "BPRS vs Classification at Cue Period")

(plot_list[["BPRS"]][["cue"]][[5]] + plot_list[["BPRS"]][["cue"]][[6]])  +
  plot_annotation(title = "BPRS vs Classification at Cue Period")

cor.test(individual_trial_averages_probs[["low_incorrect"]]$V6,indiv_avg_over_time$omnibus_span)
cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V6,indiv_avg_over_time$omnibus_span)

cor.test(individual_trial_averages_probs[["low_incorrect"]]$V6,indiv_avg_over_time$XDFR_MRI_ACC_L3)

cor.test(individual_trial_averages_probs[["high_incorrect"]]$V6[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["high_load_correct_diff"]]$V6[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V6[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])

``` 

#### Delay 

There is a significant positive relationship between the difference between correct and incorrect trials at low load and span.

There is a significant negative relationship between classification accuracy at low load incorrect trials and accuracy positive relationship between the difference between correct and incorrect trials at low load and accuracy

There is also a trending correlation for the difference between correct and incorrect at high load trials and BPRS (excluding the outlier). 

``` {r plot specific time points from indiv - delay }


(plot_list[["omnibus"]][["delay"]][[1]] + plot_list[["omnibus"]][["delay"]][[2]]) /  
  (plot_list[["omnibus"]][["delay"]][[3]] + plot_list[["omnibus"]][["delay"]][[4]]) +
  plot_annotation(title = "Omnibus vs Classification at delay Period")

(plot_list[["omnibus"]][["delay"]][[5]] + plot_list[["omnibus"]][["delay"]][[6]])  +
  plot_annotation(title = "Omnibus vs Classification at delay Period")

(plot_list[["L3_Acc"]][["delay"]][[1]] + plot_list[["L3_Acc"]][["delay"]][[2]]) /  
  (plot_list[["L3_Acc"]][["delay"]][[3]] + plot_list[["L3_Acc"]][["delay"]][[4]]) +
  plot_annotation(title = "L3_Acc vs Classification at delay Period")

(plot_list[["L3_Acc"]][["delay"]][[5]] + plot_list[["L3_Acc"]][["delay"]][[6]])  +
  plot_annotation(title = "L3_Acc vs Classification at delay Period")

(plot_list[["BPRS"]][["delay"]][[1]] + plot_list[["BPRS"]][["delay"]][[2]]) /  
  (plot_list[["BPRS"]][["delay"]][[3]] + plot_list[["BPRS"]][["delay"]][[4]]) +
  plot_annotation(title = "BPRS vs Classification at delay Period")

(plot_list[["BPRS"]][["delay"]][[5]] + plot_list[["BPRS"]][["delay"]][[6]])  +
  plot_annotation(title = "BPRS vs Classification at delay Period")

cor.test(individual_trial_averages_probs[["low_incorrect"]]$V8,indiv_avg_over_time$omnibus_span)
cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V8,indiv_avg_over_time$omnibus)

cor.test(individual_trial_averages_probs[["low_incorrect"]]$V8,indiv_avg_over_time$XDFR_MRI_ACC_L3)
cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V8,indiv_avg_over_time$XDFR_MRI_ACC_L3)

cor.test(individual_trial_averages_probs[["high_incorrect"]]$V8[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["low_incorrect"]]$V8[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["high_load_correct_diff"]]$V8[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V8[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])

``` 

#### Probe

Omnibus span is significantly positively correlated with the difference between correct/incorrect trials at low load. 

Probability of classification at incorrect high load trials is significantly negatively correlated with BPRS at TR 11, and the difference between correct trials at high load trials and BPRS.

```{r plot specific time points from indiv - probe }

(plot_list[["omnibus"]][["probe"]][[1]] + plot_list[["omnibus"]][["probe"]][[2]]) /  
  (plot_list[["omnibus"]][["probe"]][[3]] + plot_list[["omnibus"]][["probe"]][[4]]) +
  plot_annotation(title = "Omnibus vs Classification at probe Period")

(plot_list[["omnibus"]][["probe"]][[5]] + plot_list[["omnibus"]][["probe"]][[6]])  +
  plot_annotation(title = "Omnibus vs Classification at probe Period")

(plot_list[["L3_Acc"]][["probe"]][[1]] + plot_list[["L3_Acc"]][["probe"]][[2]]) /  
  (plot_list[["L3_Acc"]][["probe"]][[3]] + plot_list[["L3_Acc"]][["probe"]][[4]]) +
  plot_annotation(title = "L3_Acc vs Classification at probe Period")

(plot_list[["L3_Acc"]][["probe"]][[5]] + plot_list[["L3_Acc"]][["probe"]][[6]])  +
  plot_annotation(title = "L3_Acc vs Classification at probe Period")

(plot_list[["BPRS"]][["probe"]][[1]] + plot_list[["BPRS"]][["probe"]][[2]]) /  
  (plot_list[["BPRS"]][["probe"]][[3]] + plot_list[["BPRS"]][["probe"]][[4]]) +
  plot_annotation(title = "BPRS vs Classification at probe Period")

(plot_list[["BPRS"]][["probe"]][[5]] + plot_list[["BPRS"]][["probe"]][[6]])  +
  plot_annotation(title = "BPRS vs Classification at probe Period")

cor.test(individual_trial_averages_probs[["low_correct"]]$V11,indiv_avg_over_time$omnibus_span)
cor.test(individual_trial_averages_probs[["low_incorrect"]]$V11,indiv_avg_over_time$omnibus_span)
cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V11,indiv_avg_over_time$omnibus_span)

cor.test(individual_trial_averages_probs[["low_load_correct_diff"]]$V11,indiv_avg_over_time$XDFR_MRI_ACC_L3)

cor.test(individual_trial_averages_probs[["high_correct"]]$V11[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["high_incorrect"]]$V11[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])
cor.test(individual_trial_averages_probs[["high_load_correct_diff"]]$V11[indiv_avg_over_time$BPRS_TOT < 70],indiv_avg_over_time$BPRS_TOT[indiv_avg_over_time$BPRS_TOT < 70])


```

```{r correlate behav to each indiv category TR for each group, warning=FALSE}

behav_classification_corr_list <- list()

for (trial_type in seq.int(1,6)){ 
  group_corrs_omnibus <- data.frame(matrix(nrow=3,ncol=14))
  rownames(group_corrs_omnibus) <- names(split_indiv_probs[["all_data"]][[trial_type]])[1:3]
  colnames(group_corrs_omnibus) <- seq.int(1,14)
  
  group_corrs_acc <- data.frame(matrix(nrow=3,ncol=14))
  rownames(group_corrs_acc) <- names(split_indiv_probs[["all_data"]][[trial_type]])[1:3]
  colnames(group_corrs_acc) <- seq.int(1,14)
  
  group_corrs_BPRS <- data.frame(matrix(nrow=3,ncol=14))
  rownames(group_corrs_BPRS) <- names(split_indiv_probs[["all_data"]][[trial_type]])[1:3]
  colnames(group_corrs_BPRS) <- seq.int(1,14)
  
  for (level in seq.int(1,3)){ 
    temp_subj <- split_indiv_probs[["all_data"]][[trial_type]][[level]][order(split_indiv_probs[["all_data"]][[trial_type]][[level]]$PTID),]
    temp_data <- data_to_plot[data_to_plot$PTID %in% split_indiv_probs[["all_data"]][[trial_type]][[level]]$PTID,]
    
    for (TR in seq.int(1,14)){
      
      group_corrs_omnibus[level,TR] <- cor(temp_subj[,TR],temp_data$omnibus_span_no_DFR_MRI,use="pairwise.complete.obs")
      group_corrs_acc[level,TR] <- cor(temp_subj[,TR],temp_data$XDFR_MRI_ACC_L3,use="pairwise.complete.obs")
      group_corrs_BPRS[level,TR] <- cor(temp_subj[,TR],temp_data$BPRS_TOT.x,use="pairwise.complete.obs")
      
    }
    group_corrs_acc$level <- factor(rownames(group_corrs_acc))
    group_corrs_BPRS$level <- factor(rownames(group_corrs_acc))
    group_corrs_omnibus$level <- factor(rownames(group_corrs_acc))
    
  }
  
  behav_classification_corr_list[["omnibus"]][[names(split_indiv_probs[["all_data"]])[trial_type]]] <- group_corrs_omnibus
  behav_classification_corr_list[["BPRS"]][[names(split_indiv_probs[["all_data"]])[trial_type]]] <- group_corrs_BPRS
  behav_classification_corr_list[["L3_Acc"]][[names(split_indiv_probs[["all_data"]])[trial_type]]] <- group_corrs_acc
}

```

#### By Working Memory Capacity

```{r melt group vs behav indiv, warning=FALSE}

behav_classification_corr_melt <- list()
behav_split_plot_list <- list()

for (measure in seq.int(1,3)){
  for (trial_type in seq.int(1,6)){ 
    behav_classification_corr_melt[[names(behav_classification_corr_list)[measure]]][[names(behav_classification_corr_list[[measure]])[trial_type]]] <- melt(behav_classification_corr_list[[measure]][[trial_type]],id.vars="level")
    behav_classification_corr_melt[[measure]][[trial_type]]$variable <- as.numeric(as.character(behav_classification_corr_melt[[measure]][[trial_type]]$variable))
    behav_classification_corr_melt[[measure]][[trial_type]]$level <- factor(behav_classification_corr_melt[[measure]][[trial_type]]$level, levels=c("high","med","low"))
    
    behav_split_plot_list[[names(behav_classification_corr_melt)[measure]]][[names(behav_classification_corr_melt[[measure]])[trial_type]]] <- 
      ggplot(data = behav_classification_corr_melt[[measure]][[trial_type]],aes(x=variable,y=value))+
      geom_line(aes(color=level))+
      scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
      ggtitle(names(behav_classification_corr_list[[measure]])[trial_type])+
      xlab("TR")+
      ylab("Correlation")+
      theme_classic()
    
  }
}

```

```{r plot indiv prob vs behav by group}

(behav_split_plot_list[["omnibus"]][[1]] + behav_split_plot_list[["omnibus"]][[2]]) / 
  (behav_split_plot_list[["omnibus"]][[3]] + behav_split_plot_list[["omnibus"]][[4]])+
  plot_annotation("Omnibus Span Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["omnibus"]][[5]] + behav_split_plot_list[["omnibus"]][[6]]) + 
  plot_annotation("Omnibus Span Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["L3_Acc"]][[1]] + behav_split_plot_list[["L3_Acc"]][[2]]) / 
  (behav_split_plot_list[["L3_Acc"]][[3]] + behav_split_plot_list[["L3_Acc"]][[4]])+
  plot_annotation("High Load Acc Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["L3_Acc"]][[5]] + behav_split_plot_list[["L3_Acc"]][[6]]) +
  plot_annotation("High Load Acc Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["BPRS"]][[1]] + behav_split_plot_list[["BPRS"]][[2]]) / 
  (behav_split_plot_list[["BPRS"]][[3]] + behav_split_plot_list[["BPRS"]][[4]])+
  plot_annotation("BPRS Total Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["BPRS"]][[5]] + behav_split_plot_list[["BPRS"]][[6]]) +
  plot_annotation("BPRS Total Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")


```

## Template

### Averaged over time

If we average over time, the only significant relationship is a negative correlation between high load accuracy and the difference between correct and incorrect trials at high load and the positive relationship between span and classification at low load incorrect trials. 

```{r make plots to correlate template over time}

template_avg_over_time <- data.frame(high_correct = rowMeans(averages_from_template[["high_correct"]][,1:14]),
                                     high_incorrect = rowMeans(averages_from_template[["high_incorrect"]][,1:14]),
                                     low_correct = rowMeans(averages_from_template[["low_correct"]][,1:14]),
                                     low_incorrect = rowMeans(averages_from_template[["low_incorrect"]][,1:14],na.rm=TRUE), 
                                     high_load_diff_correct = rowMeans(averages_from_template[["high_load_correct_diff"]][,1:14]),
                                     low_load_diff_correct = rowMeans(averages_from_template[["low_load_correct_diff"]][,1:14]))

template_avg_over_time[is.na(template_avg_over_time)] <- NA 
template_avg_over_time <- data.frame(template_avg_over_time, omnibus_span = constructs_fMRI$omnibus_span_no_DFR_MRI[c(1:9,11:170)], PTID = constructs_fMRI$PTID[c(1:9,11:170)])
template_avg_over_time <- merge(template_avg_over_time, p200_data[,c("PTID","BPRS_TOT","XDFR_MRI_ACC_L3", "XDFR_MRI_ACC_L1")],by="PTID")


plot_list <- list()

for (i in seq.int(1,6)){
  plot_data <- template_avg_over_time[,c(i+1,8:11)]
  colnames(plot_data)[1] <- "prob"
  plot_list[["omnibus"]][[i]] <- ggplot(data = plot_data,aes(y=prob,x=omnibus_span))+
    geom_point()+
    stat_smooth(method="lm")+
    xlab("Probability")+
    ggtitle(colnames(template_avg_over_time)[i+1])+
    theme_classic()
  
  plot_list[["DFR_Acc"]][[i]] <- ggplot(data = plot_data,aes(y=prob,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    xlab("Probability")+
    ggtitle(colnames(template_avg_over_time)[i+1])+
    theme_classic()
  
  plot_list[["BPRS"]][[i]] <- ggplot(data = plot_data,aes(y=prob,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    xlab("Probability")+
    ggtitle(colnames(template_avg_over_time)[i+1])+
    theme_classic()
  
}

(plot_list[["omnibus"]][[1]] + plot_list[["omnibus"]][[2]]) /
  (plot_list[["omnibus"]][[3]] + plot_list[["omnibus"]][[4]]) + 
  plot_annotation(title="Correlation of face probability and Omnibus Span")

(plot_list[["omnibus"]][[5]] + plot_list[["omnibus"]][[6]])+
  plot_annotation(title="Correlation of difference in face probability across correctness and Omnibus Span")

(plot_list[["DFR_Acc"]][[1]] + plot_list[["DFR_Acc"]][[2]]) /
  (plot_list[["DFR_Acc"]][[3]] + plot_list[["DFR_Acc"]][[4]]) + 
  plot_annotation(title="Correlation of face probability and DFR High Load Accuracy")

(plot_list[["DFR_Acc"]][[5]] + plot_list[["DFR_Acc"]][[6]])+
  plot_annotation(title="Correlation of difference in face probability across correctness and DFR High Load Accuracy")

(plot_list[["BPRS"]][[1]] + plot_list[["BPRS"]][[2]]) /
  (plot_list[["BPRS"]][[3]] + plot_list[["BPRS"]][[4]]) + 
  plot_annotation(title="Correlation of face probability and BPRS")
(plot_list[["BPRS"]][[5]] + plot_list[["BPRS"]][[6]])+
  plot_annotation(title="Correlation of difference in face probability across correctness and BPRS")

cor.test(template_avg_over_time$high_incorrect, template_avg_over_time$omnibus_span)
cor.test(template_avg_over_time$low_incorrect, template_avg_over_time$omnibus_span)
cor.test(template_avg_over_time$high_load_diff_correct, template_avg_over_time$omnibus_span)
cor.test(template_avg_over_time$low_load_diff_correct, template_avg_over_time$omnibus_span)

cor.test(template_avg_over_time$high_load_diff_correct, template_avg_over_time$XDFR_MRI_ACC_L3)


```

### All subjects

#### Over time 

```{r make template correlations with behav across time for all subj, warning = FALSE}

data_to_plot <- merge(constructs_fMRI,p200_data,by="PTID")
data_to_plot <- merge(data_to_plot,p200_clinical_zscores,by="PTID")

data_to_plot <- data_to_plot[c(1:9,11:170),c(1,7,14,15,41,42)]
data_to_plot$ACC_LE <- data_to_plot$XDFR_MRI_ACC_L3 - data_to_plot$XDFR_MRI_ACC_L1

corr_to_behav_plots <- list()

for (i in seq.int(1,6)){
  measure_by_time <- data.frame(matrix(nrow=4,ncol=14))
  
  for (measure in seq.int(2,5)){
    for (TR in seq.int(1,14)){
      measure_by_time[measure-1,TR] <- cor(data_to_plot[,measure],averages_from_template[[i]][,TR],use = "pairwise.complete.obs")
    }
  }
  
  measure_by_time <- data.frame(t(measure_by_time))
  measure_by_time$TR <- seq.int(1,14)
  
  colnames(measure_by_time)[1:4] <- colnames(data_to_plot)[2:5]
  
  melted_measure_by_time <- melt(measure_by_time,id.vars="TR")
  
  corr_to_behav_plots[[names(averages_from_template)[i]]] <- ggplot(data=melted_measure_by_time,aes(x=TR,y=value))+
    geom_line(aes(color=variable))+
    scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
    ggtitle(names(averages_from_template)[i])+
    theme_classic()
  
}
```

```{r print TR template correlation all subj plots}

(corr_to_behav_plots[[1]] + corr_to_behav_plots[[2]]) / (corr_to_behav_plots[[3]] + corr_to_behav_plots[[4]])+
  plot_layout(guides="collect")+
  plot_annotation(title = "Correlation between face classification and behavioral measures")


(corr_to_behav_plots[[5]] + corr_to_behav_plots[[6]])+
  plot_layout(guides="collect")+
  plot_annotation(title = "Correlation between face classification and behavioral measures")


```

```{r pull out specfic time points from template correlation}

plot_list <- list()

for(trial_type in seq.int(1,6)){ 
  temp_plot_data <- merge(p200_data, averages_from_template[[trial_type]],by="PTID")
  temp_plot_data <- merge(temp_plot_data,constructs_fMRI,by="PTID")
  
  plot_list[["omnibus"]][["cue"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V6,x=omnibus_span_no_DFR_MRI))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  plot_list[["omnibus"]][["delay"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V8,x=omnibus_span_no_DFR_MRI))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  plot_list[["omnibus"]][["probe"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V11,x=omnibus_span_no_DFR_MRI))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  # Acc
  
  plot_list[["L3_Acc"]][["cue"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V6,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  plot_list[["L3_Acc"]][["delay"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V8,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  plot_list[["L3_Acc"]][["probe"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V11,x=XDFR_MRI_ACC_L3))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  # BPRS  
  plot_list[["BPRS"]][["cue"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V6,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  plot_list[["BPRS"]][["delay"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V8,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  plot_list[["BPRS"]][["probe"]][[trial_type]] <- ggplot(data=temp_plot_data,aes(y=V11,x=BPRS_TOT))+
    geom_point()+
    stat_smooth(method="lm")+
    ylab("Probability")+
    ggtitle(names(averages_from_template)[trial_type])+
    theme_classic()
  
  
}


```

#### Encoding 

No relationships here.

```{r plot specific time points from template - encoding }

(plot_list[["omnibus"]][["cue"]][[1]] + plot_list[["omnibus"]][["cue"]][[2]]) /  
  (plot_list[["omnibus"]][["cue"]][[3]] + plot_list[["omnibus"]][["cue"]][[4]]) +
  plot_annotation(title = "Omnibus vs Classification at Cue Period")

(plot_list[["omnibus"]][["cue"]][[5]] + plot_list[["omnibus"]][["cue"]][[6]]) +
  plot_annotation(title = "Omnibus vs Classification at Cue Period")

(plot_list[["L3_Acc"]][["cue"]][[1]] + plot_list[["L3_Acc"]][["cue"]][[2]]) /  
  (plot_list[["L3_Acc"]][["cue"]][[3]] + plot_list[["L3_Acc"]][["cue"]][[4]]) +
  plot_annotation(title = "L3_Acc vs Classification at Cue Period")

(plot_list[["L3_Acc"]][["cue"]][[5]] + plot_list[["L3_Acc"]][["cue"]][[6]]) +
  plot_annotation(title = "L3_Acc vs Classification at Cue Period")

(plot_list[["BPRS"]][["cue"]][[1]] + plot_list[["BPRS"]][["cue"]][[2]]) /  
  (plot_list[["BPRS"]][["cue"]][[3]] + plot_list[["BPRS"]][["cue"]][[4]]) +
  plot_annotation(title = "BPRS vs Classification at Cue Period")

(plot_list[["BPRS"]][["cue"]][[5]] + plot_list[["BPRS"]][["cue"]][[6]]) +
  plot_annotation(title = "BPRS vs Classification at Cue Period")

cor.test(averages_from_template[["high_incorrect"]]$V6,indiv_avg_over_time$omnibus_span)
cor.test(averages_from_template[["low_incorrect"]]$V6,indiv_avg_over_time$omnibus_span)
cor.test(averages_from_template[["high_load_correct_diff"]]$V6,indiv_avg_over_time$omnibus_span)

cor.test(averages_from_template[["high_incorrect"]]$V6,indiv_avg_over_time$XDFR_MRI_ACC_L3)
cor.test(averages_from_template[["low_correct"]]$V6,indiv_avg_over_time$XDFR_MRI_ACC_L3)

``` 

#### Delay 

There are no significant relationships 

``` {r plot specific time points from template - delay }

(plot_list[["omnibus"]][["delay"]][[1]] + plot_list[["omnibus"]][["delay"]][[2]]) /  
  (plot_list[["omnibus"]][["delay"]][[3]] + plot_list[["omnibus"]][["delay"]][[4]]) +
  plot_annotation(title = "Omnibus vs Classification at delay Period")

(plot_list[["omnibus"]][["delay"]][[5]] + plot_list[["omnibus"]][["delay"]][[6]]) +
  plot_annotation(title = "Omnibus vs Classification at delay Period")

(plot_list[["L3_Acc"]][["delay"]][[1]] + plot_list[["L3_Acc"]][["delay"]][[2]]) /  
  (plot_list[["L3_Acc"]][["delay"]][[3]] + plot_list[["L3_Acc"]][["delay"]][[4]]) +
  plot_annotation(title = "L3_Acc vs Classification at delay Period")

(plot_list[["L3_Acc"]][["delay"]][[5]] + plot_list[["L3_Acc"]][["delay"]][[6]]) +
  plot_annotation(title = "L3_Acc vs Classification at delay Period")

(plot_list[["BPRS"]][["delay"]][[1]] + plot_list[["BPRS"]][["delay"]][[2]]) /  
  (plot_list[["BPRS"]][["delay"]][[3]] + plot_list[["BPRS"]][["delay"]][[4]]) +
  plot_annotation(title = "BPRS vs Classification at delay Period")

(plot_list[["BPRS"]][["delay"]][[5]] + plot_list[["BPRS"]][["delay"]][[6]]) +
  plot_annotation(title = "BPRS vs Classification at delay Period")

cor.test(averages_from_template[["high_load_correct_diff"]]$V8,indiv_avg_over_time$omnibus_span)

cor.test(averages_from_template[["high_correct"]]$V8,indiv_avg_over_time$XDFR_MRI_ACC_L3)


``` 

#### Probe

There are no significant relationships at probe. 

```{r plot specific time points from template - probe }

(plot_list[["omnibus"]][["probe"]][[1]] + plot_list[["omnibus"]][["probe"]][[2]]) /  
  (plot_list[["omnibus"]][["probe"]][[3]] + plot_list[["omnibus"]][["probe"]][[4]]) +
  plot_annotation(title = "Omnibus vs Classification at probe Period")

(plot_list[["omnibus"]][["probe"]][[5]] + plot_list[["omnibus"]][["probe"]][[6]]) +
  plot_annotation(title = "Omnibus vs Classification at probe Period")

(plot_list[["L3_Acc"]][["probe"]][[1]] + plot_list[["L3_Acc"]][["probe"]][[2]]) /  
  (plot_list[["L3_Acc"]][["probe"]][[3]] + plot_list[["L3_Acc"]][["probe"]][[4]]) +
  plot_annotation(title = "L3_Acc vs Classification at probe Period")

(plot_list[["L3_Acc"]][["probe"]][[5]] + plot_list[["L3_Acc"]][["probe"]][[6]]) +
  plot_annotation(title = "L3_Acc vs Classification at probe Period")

(plot_list[["BPRS"]][["probe"]][[1]] + plot_list[["BPRS"]][["probe"]][[2]]) /  
  (plot_list[["BPRS"]][["probe"]][[3]] + plot_list[["BPRS"]][["probe"]][[4]]) +
  plot_annotation(title = "BPRS vs Classification at probe Period")

(plot_list[["BPRS"]][["probe"]][[5]] + plot_list[["BPRS"]][["probe"]][[6]]) +
  plot_annotation(title = "BPRS vs Classification at probe Period")

cor.test(averages_from_template[["high_correct"]]$V11,indiv_avg_over_time$omnibus_span)
cor.test(averages_from_template[["high_load_correct_diff"]]$V11,indiv_avg_over_time$omnibus_span)


```

```{r correlate behav to each template TR for each group, warning=FALSE}

behav_classification_corr_list <- list()

for (trial_type in seq.int(1,6)){ 
  group_corrs_omnibus <- data.frame(matrix(nrow=3,ncol=14))
  rownames(group_corrs_omnibus) <- names(split_template[["all_data"]][[trial_type]])[1:3]
  colnames(group_corrs_omnibus) <- seq.int(1,14)
  
  group_corrs_acc <- data.frame(matrix(nrow=3,ncol=14))
  rownames(group_corrs_acc) <- names(split_template[["all_data"]][[trial_type]])[1:3]
  colnames(group_corrs_acc) <- seq.int(1,14)
  
  group_corrs_BPRS <- data.frame(matrix(nrow=3,ncol=14))
  rownames(group_corrs_BPRS) <- names(split_template[["all_data"]][[trial_type]])[1:3]
  colnames(group_corrs_BPRS) <- seq.int(1,14)
  
  for (level in seq.int(1,3)){ 
    temp_subj <- split_template[["all_data"]][[trial_type]][[level]][order(split_template[["all_data"]][[trial_type]][[level]]$PTID),]
    temp_data <- data_to_plot[data_to_plot$PTID %in% split_template[["all_data"]][[trial_type]][[level]]$PTID,]
    
    for (TR in seq.int(1,14)){
      
      group_corrs_omnibus[level,TR] <- cor(temp_subj[,TR],temp_data$omnibus_span_no_DFR_MRI,use="pairwise.complete.obs")
      group_corrs_acc[level,TR] <- cor(temp_subj[,TR],temp_data$XDFR_MRI_ACC_L3,use="pairwise.complete.obs")
      group_corrs_BPRS[level,TR] <- cor(temp_subj[,TR],temp_data$BPRS_TOT.x,use="pairwise.complete.obs")
      
    }
    group_corrs_acc$level <- factor(rownames(group_corrs_acc))
    group_corrs_BPRS$level <- factor(rownames(group_corrs_acc))
    group_corrs_omnibus$level <- factor(rownames(group_corrs_acc))
    
  }
  
  behav_classification_corr_list[["omnibus"]][[names(split_template[["all_data"]])[trial_type]]] <- group_corrs_omnibus
  behav_classification_corr_list[["BPRS"]][[names(split_template[["all_data"]])[trial_type]]] <- group_corrs_BPRS
  behav_classification_corr_list[["L3_Acc"]][[names(split_template[["all_data"]])[trial_type]]] <- group_corrs_acc
}

```

#### By Working Memory Capacity

```{r melt group vs behav template, warning = FALSE}

behav_classification_corr_melt <- list()
behav_split_plot_list <- list()

for (measure in seq.int(1,3)){
  for (trial_type in seq.int(1,6)){ 
    behav_classification_corr_melt[[names(behav_classification_corr_list)[measure]]][[names(behav_classification_corr_list[[measure]])[trial_type]]] <- melt(behav_classification_corr_list[[measure]][[trial_type]],id.vars="level")
    behav_classification_corr_melt[[measure]][[trial_type]]$variable <- as.numeric(as.character(behav_classification_corr_melt[[measure]][[trial_type]]$variable))
    behav_classification_corr_melt[[measure]][[trial_type]]$level <- factor(behav_classification_corr_melt[[measure]][[trial_type]]$level, levels=c("high","med","low"))
    
    behav_split_plot_list[[names(behav_classification_corr_melt)[measure]]][[names(behav_classification_corr_melt[[measure]])[trial_type]]] <- 
      ggplot(data = behav_classification_corr_melt[[measure]][[trial_type]],aes(x=variable,y=value))+
      geom_line(aes(color=level))+
      scale_x_continuous(breaks = c(1:14),labels=c(1:14))+
      ggtitle(names(behav_classification_corr_list[[measure]])[trial_type])+
      xlab("TR")+
      ylab("Correlation")+
      theme_classic()
    
  }
}

```

```{r plot template prob vs behav by group}

(behav_split_plot_list[["omnibus"]][[1]] + behav_split_plot_list[["omnibus"]][[2]]) / 
  (behav_split_plot_list[["omnibus"]][[3]] + behav_split_plot_list[["omnibus"]][[4]])+
  plot_annotation("Omnibus Span Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["omnibus"]][[5]] + behav_split_plot_list[["omnibus"]][[6]]) + 
  plot_annotation("Omnibus Span Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["L3_Acc"]][[1]] + behav_split_plot_list[["L3_Acc"]][[2]]) / 
  (behav_split_plot_list[["L3_Acc"]][[3]] + behav_split_plot_list[["L3_Acc"]][[4]])+
  plot_annotation("High Load Acc Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["L3_Acc"]][[5]] + behav_split_plot_list[["L3_Acc"]][[6]]) + 
  plot_annotation("High Load Acc Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")


(behav_split_plot_list[["BPRS"]][[1]] + behav_split_plot_list[["BPRS"]][[2]]) / 
  (behav_split_plot_list[["BPRS"]][[3]] + behav_split_plot_list[["BPRS"]][[4]])+
  plot_annotation("BPRS Total Correlation with Face Classification Probability by Group")+
  plot_layout(guides="collect")

(behav_split_plot_list[["BPRS"]][[5]] + behav_split_plot_list[["BPRS"]][[6]]) + 
  plot_annotation("BPRS Total with Face Classification Probability by Group")+
  plot_layout(guides="collect")

```
