---
title: "WMC and DFR Split Groups Comparison"
author: "Catherine Walsh"
date: "4/8/2020"
output:
  html_document:
    toc: true 
    toc_float: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

So far, we've run a bunch of analyses on the data split two different ways - by the WM capacity scores and by the high load DFR performance. Below is a table of the summary of analyses: 

+----------------+----------------------+--------------------+
| Measure        | WM                   | DFR                |
+================+======================+====================+
| DFR delay LE   | inverted U           | linearly increases |
+----------------+----------------------+--------------------+
| constructs     | linearly increases   | linearly increases |
+----------------+----------------------+--------------------+
| clinical       | linearly decreases   | linearly decreases |
+----------------+----------------------+--------------------+
| cue period     | asymptotic           | linearly increases |
| full mask      | med,high > low in    | for L3 and LE      |
|                | LE                   |                    |
+----------------+----------------------+--------------------+
| delay period   | inverted U           | linearly increases |
| full mask      | L3 and LE            | L3 and LE          |
+----------------+----------------------+--------------------+
| delay period   | inverted U in LE     | linearly increases |
| indiv ROIs     |                      |  in LE             |
+----------------+----------------------+--------------------+
| probe period   | asymptotic           | linearly increases |
| full mask      | med,high>low in LE   | in LE              |
+----------------+----------------------+--------------------+
| FFA            | linearly increases   | linearly increases |
|                | in L cue LE          | in L cue LE        |
+----------------+----------------------+--------------------+
| HPC Posterior  | inverted U @ L3      | no effect          |
|                | L cue, delay, probe  |                    |
+----------------+----------------------+--------------------+
| RSFC           | no effect            | FPCN: med > high   |
| within network |                      | VAN: low > high    |
+----------------+----------------------+--------------------+
| RSFC           | inverted U           | no effects         |
| across network | FPCN/CO              |                    |
+----------------+----------------------+--------------------+
| Beta Series    | no effect            | linearly increases |
| connectivity   |                      | L3: FPCN/FFA,      |
| cue            |                      | FPCN/HPC, HPC/FFA  |
|                |                      | LE: FPCN/FPCN,     |
|                |                      | FPCN/FFA           |
+----------------+----------------------+--------------------+
| Beta Series    | LE: inverted U in    | linearly decreases |
| connectivity   | HPC/FFA              | L3: FPCN/HPC       |
| delay          |                      |                    |
+----------------+----------------------+--------------------+
| BCT measures   | mean participation   | no effect          |
|                | coefficient:         |                    |
|                | U shaped             |                    |
|                | DMN: U shaped        |                    |
|                | VAN: linear increase |                    |
+----------------+----------------------+--------------------+

```{r load libraries, data and custom functions}

library(dplyr)
library(ggplot2)
library(reshape2)
library(psych)
library(patchwork)
library(R.matlab)

load('data/load_effects_DFR.RData')
load('data/behav.RData')
load('data/structural_measures.RData')
load('data/connectivity_data.RData')
load('data/DFR_split_groups_info.RData')
load('data/split_WM_groups_fMRI.RData')

source('helper_fxns/load_in_ROI.R')
source('helper_fxns/split_TC_into_groups.R')
source('helper_fxns/create_TC_for_plot.R')

# these times are based on when the actual cues were on the screen 
rects <- data.frame(xstart=c(0,2.5,10),xend=c(2.5,10,12),col = factor(c("cue","delay","probe"),levels=c("cue","delay","probe")))

# adjust for hemodynamic delay 
rects$xstart <- rects$xstart+5
rects$xend <- rects$xend+5


```

# Regressions 

Interestingly, it looks like there is ovearchingly a linear relationship between these measures and DFR performance, with an inverted U-shape relationship with capacity. Let's see if these relationships hold up when we include both of them in a model, especially for the ones where there is a significant relationship with both variables. For the WM capacity, we're going to add in a quadratic term to see if that fits the data. 

We're also going to regress the effect of DFR accuracy out of omnibus span and see what the residuals look like plotted against our variables of interest. 

```{r create a base data}

base_data <- merge(p200_data,constructs_fMRI,by="PTID")
# want to create a base data that we can include in models - DFR accuracy, WM capacity and gender, age and WHODAS scores as covariates 
base_data <- dplyr::select(base_data,PTID,"XDFR_MRI_ACC_L3","omnibus_span_no_DFR_MRI","X010701_GENDER","PX010101_AGE","WHO_ST_S32")
colnames(base_data) <- c("PTID","DFR_L3_ACC","omnibus_span", "gender", "age", "WHODAS")
base_data$span_sq <- base_data$omnibus_span^2
base_data <- merge(base_data,p200_demographics[,c(1,4)])

# shift to dummy coding 
base_data$SCANNER <- base_data$SCANNER - 1
base_data$gender <- base_data$gender - 1 

# one subject did not report gender - assign 0.5 as to not mess with the regression too much
base_data$gender[73] <- 0.5

# remove subjects with incomplete data 
base_data <- base_data[c(1,90,92:105,107:170),]

```

For findings where DFR is significant, can try to regess it out of omnibus and plot that against variable of interest to see if inverted U shape is still present, since I'm not sure span^2 is the right measure. 

```{r get omnibus residuals}

omnibus.lm <- lm(omnibus_span ~ DFR_L3_ACC + gender + age + WHODAS + SCANNER, data= base_data)
summary(omnibus.lm)

base_data$omnibus_resid <- resid(omnibus.lm)

```

## Cue Period Load Effect

```{r cue period full mask - LE }

full_mask_data <- merge(base_data,p200_DFR_full_mask)

cue_loadEffect_DFR.lm <- lm(cue_loadEffect ~ DFR_L3_ACC + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(cue_loadEffect_DFR.lm)

cue_loadEffect_span.lm <- lm(cue_loadEffect ~ omnibus_span + span_sq + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(cue_loadEffect_span.lm)

cue_loadEffect_all.lm <- lm(cue_loadEffect ~ omnibus_span + span_sq + DFR_L3_ACC + gender + age + WHODAS + SCANNER, data = full_mask_data)
summary(cue_loadEffect_all.lm)

```

```{r omnibus resid vs cue LE}

no_resid <- ggplot(data = full_mask_data, aes(x=omnibus_span,y=cue_loadEffect))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR not regressed")

resid <- ggplot(data = full_mask_data, aes(x=omnibus_resid,y=cue_loadEffect))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR regressed")

no_resid + resid+
  plot_annotation(title = "Cue Load Effect")

cor.test(full_mask_data$omnibus_resid,full_mask_data$cue_loadEffect)


```

## Delay Period 

Interestingly, the delay period is the only finding that had an inverted U-shape relationship with capacity that held up when we regressed out the effects of accuracy. 

### High Load 

```{r delay period full mask - L3}


delay_high_DFR.lm <- lm(delay_high ~ DFR_L3_ACC + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(delay_high_DFR.lm)

delay_high_span.lm <- lm(delay_high ~ omnibus_span + span_sq + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(delay_high_span.lm)

delay_high_all.lm <- lm(delay_high ~ omnibus_span + span_sq + DFR_L3_ACC + gender + age + WHODAS + SCANNER, data = full_mask_data)
summary(delay_high_all.lm)


```

```{r omnibus resid vs delay L3}

no_resid <- ggplot(data = full_mask_data, aes(x=omnibus_span,y=delay_high))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR not regressed")

resid <- ggplot(data = full_mask_data, aes(x=omnibus_resid,y=delay_high))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR regressed")

no_resid + resid+
  plot_annotation(title = "Delay High Load")
cor.test(full_mask_data$omnibus_resid,full_mask_data$delay_high)


```

### Load Effect

```{r delay period full mask - LE}

delay_loadEffect_DFR.lm <- lm(delay_loadEffect ~ DFR_L3_ACC + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(delay_loadEffect_DFR.lm)

delay_loadEffect_span.lm <- lm(delay_loadEffect ~ omnibus_span + span_sq + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(delay_loadEffect_span.lm)

delay_loadEffect_all.lm <- lm(delay_loadEffect ~ omnibus_span + span_sq + DFR_L3_ACC + gender + age + WHODAS + SCANNER, data = full_mask_data)
summary(delay_loadEffect_all.lm)

```

```{r omnibus resid vs delay LE}

no_resid <- ggplot(data = full_mask_data, aes(x=omnibus_span,y=delay_loadEffect))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR not regressed")

resid <- ggplot(data = full_mask_data, aes(x=omnibus_resid,y=delay_loadEffect))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR regressed")

no_resid + resid+
  plot_annotation(title = "Delay Load Effect")

cor.test(full_mask_data$omnibus_resid,full_mask_data$delay_loadEffect)


```

## Probe Period LE

```{r probe period full mask}

probe_loadEffect_DFR.lm <- lm(probe_loadEffect ~ DFR_L3_ACC + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(probe_loadEffect_DFR.lm)

probe_loadEffect_span.lm <- lm(probe_loadEffect ~ omnibus_span + span_sq + gender + age + WHODAS + SCANNER, data= full_mask_data)
summary(probe_loadEffect_span.lm)

probe_loadEffect_all.lm <- lm(probe_loadEffect ~ omnibus_span + span_sq + DFR_L3_ACC + gender + age + WHODAS + SCANNER, data = full_mask_data)
summary(probe_loadEffect_all.lm)

```

```{r omnibus resid vs probe LE}

no_resid <- ggplot(data = full_mask_data, aes(x=omnibus_span,y=probe_loadEffect))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR not regressed")

resid <- ggplot(data = full_mask_data, aes(x=omnibus_resid,y=probe_loadEffect))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR regressed")

no_resid + resid+
  plot_annotation(title = "Probe Load Effect")

cor.test(full_mask_data$omnibus_resid,full_mask_data$probe_loadEffect)

```

## FFA

Looking at the load effect in the L FFA during the cue period. 

```{r FFA}

FFA_data <- merge(base_data,p200_FFA)

FFA_loadEffect_DFR.lm <- lm(L_CUE_LE ~ DFR_L3_ACC + gender + age + WHODAS + SCANNER, data= FFA_data)
summary(FFA_loadEffect_DFR.lm)

FFA_loadEffect_span.lm <- lm(L_CUE_LE ~ omnibus_span + gender + age + WHODAS + SCANNER, data= FFA_data)
summary(FFA_loadEffect_span.lm)

FFA_loadEffect_all.lm <- lm(L_CUE_LE ~ omnibus_span +  DFR_L3_ACC + gender + age + WHODAS + SCANNER, data = FFA_data)
summary(FFA_loadEffect_all.lm)


```

```{r omnibus resid vs L FFA cue LE}

no_resid <- ggplot(data = FFA_data, aes(x=omnibus_span,y=L_CUE_LE))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR not regressed")

resid <- ggplot(data = FFA_data, aes(x=omnibus_resid,y=L_CUE_LE))+
  geom_point()+
  stat_smooth(method="loess")+
  ggtitle("DFR regressed")

no_resid + resid+
  plot_annotation(title = "L FFA - cue LE")

cor.test(FFA_data$omnibus_resid,FFA_data$L_CUE_LE)

```

# Time courses 

```{r create 6 groups}

HL <- split_constructs[["low"]][split_constructs[["low"]]$PTID %in% DFR_median_split_groups[["high"]]$PTID,]
HL$level <- "HL"
HM <- split_constructs[["med"]][split_constructs[["med"]]$PTID %in% DFR_median_split_groups[["high"]]$PTID,]
HM$level <- "HM"
HH <- split_constructs[["high"]][split_constructs[["high"]]$PTID %in% DFR_median_split_groups[["high"]]$PTID,]
HH$level <- "HH"

LL <- split_constructs[["low"]][split_constructs[["low"]]$PTID %in% DFR_median_split_groups[["low"]]$PTID,]
LL$level <- "LL"
LM <- split_constructs[["med"]][split_constructs[["med"]]$PTID %in% DFR_median_split_groups[["low"]]$PTID,]
LM$level <- "LM"
LH <- split_constructs[["high"]][split_constructs[["high"]]$PTID %in% DFR_median_split_groups[["low"]]$PTID,]
LH$level <- "LH"

things_to_hist <- rbind(HL,HM,HH,LL,LM,LH)

six_groups <- list(HL = data.frame(HL), HM = data.frame(HM), HH = data.frame(HH), LL = data.frame(LL), LM = data.frame(LM), LH = data.frame(LH), all = data.frame(things_to_hist))

```

```{r load in time course data}

basepath <- "~/Documents/UCLA/Research/RDoC/TimeCourseData/"

# delay period 

delay_ROI_list <- c("L_dlPFC", "L_aMFG", "L_dMFG", "L_IPS", "L_preSMA", "R_dlPFC", "R_dMFG",
                    "R_IPS", "R_medParietal")

delay_TCs <- load_in_ROI(basepath, delay_ROI_list)

# cue 

cue_ROI_list <- c("cue_R_preSMA", "cue_R_occipital", "cue_R_MFG", "cue_R_IPS", "cue_R_insula", 
                  "cue_R_FEF", "cue_L_occipital", "cue_L_IPS", "cue_L_insula", "cue_L_FEF")

cue_TCs <- load_in_ROI(basepath, cue_ROI_list)

# probe 

probe_ROI_list <- c("probe_R_OFC", "probe_R_insula", "probe_R_dlPFC", "probe_L_IPS", "probe_L_insula",
                    "probe_L_dlPFC", "probe_L_aMFG", "probe_dmPFC")

probe_TCs <- load_in_ROI(basepath, probe_ROI_list)

```

```{r split TCs into groups}

allSubjs <- constructs_fMRI$PTID

split_cue_six_groups <- split_TC_into_groups(cue_TCs,six_groups,allSubjs,group_names=c("HL","HM","HH", "LL", "LM", "LH"))
split_delay_six_groups <- split_TC_into_groups(delay_TCs,six_groups,allSubjs,group_names=c("HL","HM","HH", "LL", "LM", "LH"))
split_probe_six_groups <- split_TC_into_groups(probe_TCs,six_groups,allSubjs,group_names=c("HL","HM","HH", "LL", "LM", "LH"))

```

```{r prep TCs for plotting}

cue_TC_for_plot <- create_TC_for_plot(split_cue_six_groups)
delay_TC_for_plot <- create_TC_for_plot(split_delay_six_groups)
probe_TC_for_plot <- create_TC_for_plot(split_probe_six_groups)

```

## L1 vs L3 activity 

Here, we're plotting our data split into 6 groups - based on both WM capacity and a median split DFR performance. 

Groups are labeled by this split - the first letter (H/L) is the DFR split and the second letter (H/M/L) is the WM split. 

### Cue 

```{r plot L1 vs L3 -- cue}

for (ROI in seq.int(1,length(cue_TC_for_plot))){
  print(ggplot(data=cue_TC_for_plot[[ROI]][["wide"]]) + 
          geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf, fill=col), alpha =0.4,show.legend = FALSE)+
          geom_line(aes(x=Time,y=L3,color=level),size=1)+
          geom_line(aes(x=Time,y=L1,color=level),size=1,linetype="dashed")+
          ylab("Mean Activity") + 
          ggtitle(paste0("L3 vs L1 - ",names(cue_TC_for_plot)[ROI]))+
          ylim(c(-.4,.6)))
}



```

### Delay

```{r plot L1 vs L3 -- delay}

for (ROI in seq.int(1,length(delay_TC_for_plot))){
  print(ggplot(data=delay_TC_for_plot[[ROI]][["wide"]]) + 
          geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf, fill=col), alpha =0.4,show.legend = FALSE)+
          geom_line(aes(x=Time,y=L3,color=level),size=1)+
          geom_line(aes(x=Time,y=L1,color=level),size=1,linetype="dashed")+
          ylab("Mean Activity") + 
          ggtitle(paste0("L3 vs L1 - ",names(delay_TC_for_plot)[ROI]))+
          ylim(c(-.4,.6)))
}



```

### Probe 

```{r plot L1 vs L3 - probe}

for (ROI in seq.int(1,length(probe_TC_for_plot))){
  print(ggplot(data=probe_TC_for_plot[[ROI]][["wide"]]) + 
          geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf, fill=col), alpha =0.4,show.legend = FALSE)+
          geom_line(aes(x=Time,y=L3,color=level),size=1)+
          geom_line(aes(x=Time,y=L1,color=level),size=1,linetype="dashed")+
          ylab("Mean Activity") + 
          ggtitle(paste0("L3 vs L1 - ",names(probe_TC_for_plot)[ROI]))+
          ylim(c(-.4,.6)))
}

```

## Load Effects 

### Cue 

```{r plot LE - cue}

for (ROI in seq.int(1,length(cue_TC_for_plot))){
  print(ggplot(data=cue_TC_for_plot[[ROI]][["wide"]]) +
          geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
          geom_line(aes(x=Time,y=LE,color=level),size=1)+
          geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load == "LE"),aes(x=Time,ymin=SE_min,ymax=SE_max,fill=level),alpha=.2,linetype=2)+
          ylab("Mean Activity") +
          ggtitle(paste0("LE - ",names(cue_TC_for_plot)[ROI]))+
          ylim(c(-.4,.6))
  )
}

```

### Delay 

```{r plot LE - delay}

for (ROI in seq.int(1,length(delay_TC_for_plot))){
  print(ggplot(data=delay_TC_for_plot[[ROI]][["wide"]]) +
          geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
          geom_line(aes(x=Time,y=LE,color=level),size=1)+
          geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load == "LE"),aes(x=Time,ymin=SE_min,ymax=SE_max,fill=level),alpha=.2,linetype=2)+
          ylab("Mean Activity") +
          ggtitle(paste0("LE - ",names(delay_TC_for_plot)[ROI]))+
          ylim(c(-.4,.6))
  )
}

```

### Probe

```{r plot LE - probe}

for (ROI in seq.int(1,length(probe_TC_for_plot))){
  print(ggplot(data=probe_TC_for_plot[[ROI]][["wide"]]) +
          geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
          geom_line(aes(x=Time,y=LE,color=level),size=1)+
          geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load == "LE"),aes(x=Time,ymin=SE_min,ymax=SE_max,fill=level),alpha=.2,linetype=2)+
          ylab("Mean Activity") +
          ggtitle(paste0("LE - ",names(probe_TC_for_plot)[ROI]))+
          ylim(c(-.4,.6))
  )
}

```

## Split on DFR 

To be able to compare across groups better, let's split high performing and low performing groups onto different graphs. 

### Cue 

```{r plot split on DFR - cue}

low_col = c("turquoise","blue","violet")
high_col = c("red","gold","green")

for (ROI in seq.int(1,length(cue_TC_for_plot))){
  low <- ggplot(data=cue_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LL" | level == "LM" | level == "LH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="turquoise")+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="blue")+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="violet")+
    ylab("Mean Activity") +
    ggtitle("Low Performing Subjects")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=low_col)
  
  high <- ggplot(data=cue_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "HL" | level == "HM" | level == "HH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HL"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="red",alpha=.2,linetype=2)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HM"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="gold",alpha=.2,linetype=2)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HH"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="green",alpha=.2,linetype=2)+
    ylab("Mean Activity") +
    ggtitle("High Performing Subjects")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=high_col)
  
  print((low + high) +
          plot_annotation(title= names(cue_TC_for_plot)[[ROI]])+
          plot_layout(guides = "collect"))
  
} 

```

### Delay 

```{r plot split on DFR - delay}

low_col = c("turquoise","blue","violet")
high_col = c("red","gold","green")

for (ROI in seq.int(1,length(delay_TC_for_plot))){
  low <- ggplot(data=delay_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LL" | level == "LM" | level == "LH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="turquoise")+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="blue")+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="violet")+
    ylab("Mean Activity") +
    ggtitle("Low Performing Subjects")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=low_col)
  
  high <- ggplot(data=delay_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "HL" | level == "HM" | level == "HH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HL"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="red",alpha=.2,linetype=2)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HM"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="gold",alpha=.2,linetype=2)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HH"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="green",alpha=.2,linetype=2)+
    ylab("Mean Activity") +
    ggtitle("High Performing Subjects")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=high_col)
  
  print((low + high) +
          plot_annotation(title= names(delay_TC_for_plot)[[ROI]])+
          plot_layout(guides = "collect"))
  
} 

```

### Probe 

```{r plot split on DFR - probe}

low_col = c("turquoise","blue","violet")
high_col = c("red","gold","green")

for (ROI in seq.int(1,length(probe_TC_for_plot))){
  low <- ggplot(data=probe_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LL" | level == "LM" | level == "LH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="turquoise")+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="blue")+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="violet")+
    ylab("Mean Activity") +
    ggtitle("Low Performing Subjects")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=low_col)
  
  high <- ggplot(data=probe_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "HL" | level == "HM" | level == "HH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HL"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="red",alpha=.2,linetype=2)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HM"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="gold",alpha=.2,linetype=2)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HH"),aes(x=Time,ymin=SE_min,ymax=SE_max),fill="green",alpha=.2,linetype=2)+
    ylab("Mean Activity") +
    ggtitle("High Performing Subjects")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=high_col)
  
  print((low + high) +
          plot_annotation(title= names(probe_TC_for_plot)[[ROI]])+
          plot_layout(guides = "collect"))
  
} 

```

## Split on WM 

Same idea, but split on WMC.

### Cue 

```{r plot split on WM - cue}

low_col <- c("red","turquoise")
med_col <- c("gold","blue")
high_col <- c("green","violet")

for (ROI in seq.int(1,length(cue_TC_for_plot))){
  low <- ggplot(data=cue_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LL" | level == "HL")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="turquoise")+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="red")+
    ylab("Mean Activity") +
    ggtitle("Low WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=low_col)
  
  med <- ggplot(data=cue_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LM" | level == "HM")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="blue")+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="gold")+
    ylab("Mean Activity") +
    ggtitle("Med WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=med_col)
  
  high <- ggplot(data=cue_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LH" | level == "HH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="violet")+
    geom_ribbon(data=cue_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="green")+
    ylab("Mean Activity") +
    ggtitle("High WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=high_col)
  
  print((low + med + high) +
          plot_annotation(title= names(cue_TC_for_plot)[[ROI]])+
          plot_layout(guides = "collect")
  )
  
} 

```

### Delay 

```{r plot split on WM - delay}

low_col <- c("red","turquoise")
med_col <- c("gold","blue")
high_col <- c("green","violet")

for (ROI in seq.int(1,length(delay_TC_for_plot))){
  low <- ggplot(data=delay_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LL" | level == "HL")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="turquoise")+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="red")+
    ylab("Mean Activity") +
    ggtitle("Low WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=low_col)
  
  med <- ggplot(data=delay_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LM" | level == "HM")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="blue")+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="gold")+
    ylab("Mean Activity") +
    ggtitle("Med WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=med_col)
  
  high <- ggplot(data=delay_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LH" | level == "HH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="violet")+
    geom_ribbon(data=delay_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="green")+
    ylab("Mean Activity") +
    ggtitle("High WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=high_col)
  
  print((low + med + high) +
          plot_annotation(title= names(delay_TC_for_plot)[[ROI]])+
          plot_layout(guides = "collect"))
  
} 

```

### Probe 

```{r plot split on WM - probe}

low_col <- c("red","turquoise")
med_col <- c("gold","blue")
high_col <- c("green","violet")

for (ROI in seq.int(1,length(probe_TC_for_plot))){
  low <- ggplot(data=probe_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LL" | level == "HL")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="turquoise")+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HL"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="red")+
    ylab("Mean Activity") +
    ggtitle("Low WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=low_col)
  
  med <- ggplot(data=probe_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LM" | level == "HM")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="blue")+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HM"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="gold")+
    ylab("Mean Activity") +
    ggtitle("Med WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=med_col)
  
  high <- ggplot(data=probe_TC_for_plot[[ROI]][["wide"]] %>% filter(level == "LH" | level == "HH")) +
    geom_rect(data=rects,aes(xmin=xstart, xmax=xend, ymin = -Inf, ymax=Inf), fill="grey", alpha =0.4,show.legend = FALSE)+
    geom_line(aes(x=Time,y=LE,color=level),size=1)+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "LH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="violet")+
    geom_ribbon(data=probe_TC_for_plot[[ROI]][["long"]] %>% filter(load=="LE") %>% filter(level == "HH"),aes(x=Time,ymin=SE_min,ymax=SE_max),alpha=.2,linetype=2,fill="green")+
    ylab("Mean Activity") +
    ggtitle("High WMC")+
    ylim(c(-.2,.4))+
    scale_colour_manual(values=high_col)
  
  print((low + med + high) +
          plot_annotation(title= names(probe_TC_for_plot)[[ROI]])+
          plot_layout(guides = "collect"))
  
} 

```
