---
title: "Extreme Groups Split Means"
author: "Catherine Walsh"
date: "4/1/2020"
output:
  html_document:
    toc: true 
    toc_float: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Another question we had was to see whether splitting into smaller, more extreme groups would show morer extreme differences across them. 

```{r load libraries, data and custom functions}

library(dplyr)
library(ggplot2)
library(reshape2)
library(psych)
library(patchwork)
library(rockchalk)

load('data/load_effects_DFR.RData')
load('data/behav.RData')
load('data/structural_measures.RData')
load('data/connectivity_data.RData')

source("helper_fxns/split_into_groups.R")
source("helper_fxns/prep_split_for_bar_plots.R")
source("helper_fxns/plot_bars.R")

```

```{r create more exteme groups based on omnibus span, echo=FALSE}

p200_constructs_sorted <- constructs_fMRI[order(constructs_fMRI$omnibus_span_no_DFR_MRI),]

low_extreme <- p200_constructs_sorted[1:40,]
med_extreme <- p200_constructs_sorted[65:104,]
high_extreme <- p200_constructs_sorted[131:170,]

low_extreme$level <- "low"
med_extreme$level <- "med"
high_extreme$level <- "high"

things_to_hist <- rbind(low_extreme,med_extreme,high_extreme)
extreme_groups <- list(high = data.frame(high_extreme), med = data.frame(med_extreme), low = data.frame(low_extreme), all = data.frame(things_to_hist))

save(extreme_groups, file = "data/extreme_split_groups_info.RData")

```

```{r scatter plots constructs to load effects}

constructs_fMRI <- construct_vars_omnibus[construct_vars_omnibus$PTID %in% p200_indiv_ROI_DFR_delay$PTID,]

data_for_plot <- merge(p200_indiv_ROI_DFR_delay,constructs_fMRI)
data_for_plot <- merge(data_for_plot,things_to_hist[,c(1,8)],by="PTID",all=TRUE)

data_for_plot$level <- factor(data_for_plot$level, levels = c("high","med","low"))

p1 <- ggplot(data_for_plot, aes(x=omnibus_span_no_DFR_MRI, y = DFR_ROIs))+
  geom_point(aes(color=level))+
  stat_smooth(method="loess")

p2 <- ggplot(data_for_plot, aes(x=omnibus_span_no_DFR_MRI, y = DFR_L_dlPFC))+
  geom_point(aes(color=level))+
  stat_smooth(method="loess")

p3 <- ggplot(data_for_plot, aes(x=omnibus_span_no_DFR_MRI, y = DFR_L_IPS))+
  geom_point(aes(color=level))+
  stat_smooth(method="loess")


p4 <- ggplot(data_for_plot, aes(x=omnibus_span_no_DFR_MRI, y = DFR_L_preSMA))+
  geom_point(aes(color=level))+
  stat_smooth(method="loess")

(p1+p2)/(p3+p4)


```


```{r split load effects data into groups}

split_constructs <- split_into_groups(constructs_fMRI[1:7],extreme_groups)
split_clinical <- split_into_groups(p200_clinical_zscores, extreme_groups)
split_DFR_delay <- split_into_groups(p200_indiv_ROI_DFR_delay, extreme_groups)
split_DFR_cue <- split_into_groups(p200_indiv_ROI_DFR_cue, extreme_groups)
split_DFR_probe <- split_into_groups(p200_indiv_ROI_DFR_probe, extreme_groups)
split_DFR_FFA <- split_into_groups(p200_FFA,extreme_groups)
split_DFR_HPC_Ant <- split_into_groups(p200_HPC_Ant, extreme_groups)
split_DFR_HPC_Med <- split_into_groups(p200_HPC_Med, extreme_groups)
split_DFR_HPC_Post <- split_into_groups(p200_HPC_Post, extreme_groups)
split_fullMask_delay <- split_into_groups(p200_DFR_full_mask, extreme_groups)
split_cue_ROIs <- split_into_groups(p200_indiv_ROI_delayDFR_cuePeriod, extreme_groups)
split_demographics <- split_into_groups(p200_demographics,extreme_groups)
split_cortical_thickness_DFR <- split_into_groups(p200_DFR_fullMask_cortical_thickness,extreme_groups)
split_RS <- split_into_groups(p200_all_RS,extreme_groups)
split_beta_conn_cue <- split_into_groups(p200_beta_conn_cue,extreme_groups)
split_beta_conn_delay <- split_into_groups(p200_beta_conn_delay,extreme_groups)
split_BCT <- split_into_groups(p200_BCT_forCorr,extreme_groups)
split_indiv_partic_coeff <- split_into_groups(p200_indiv_network_ParticCoeff,extreme_groups)

```

```{r save split group data, eval=FALSE}

save(list=c("split_constructs","split_clinical","split_DFR_delay", "split_DFR_cue", "split_DFR_probe", "split_DFR_FFA", "split_DFR_HPC_Ant", "split_DFR_HPC_Med", "split_DFR_HPC_Post", "split_fullMask_delay", "split_cue_ROIs", "split_demographics","split_cortical_thickness_DFR","split_RS","split_beta_conn_cue","split_beta_conn_delay","split_BCT", "split_indiv_partic_coeff"), file="data/split_extreme_groups_fMRI.RData")

```

```{r prep demo data for plots}

split_means_demo <- data.frame(matrix(nrow=length(split_demographics)-1,ncol=8))
colnames(split_means_demo) <- c("Trio","Prisma","CS","NCS","female","male","age","age_se")
rownames(split_means_demo) <- names(split_demographics)[1:length(names(split_demographics))-1]

for (level in seq.int(1,length(split_demographics)-1)){
  split_means_demo$Trio[level] <- length(split_demographics[[level]]$SCANNER[split_demographics[[level]]$SCANNER==1])
  split_means_demo$Prisma[level] <- length(split_demographics[[level]]$SCANNER[split_demographics[[level]]$SCANNER==2])
  split_means_demo$CS[level] <- length(split_demographics[[level]]$GROUP[split_demographics[[level]]$GROUP==1])
  split_means_demo$NCS[level] <- length(split_demographics[[level]]$GROUP[split_demographics[[level]]$GROUP==2])
  split_means_demo$female[level] <- length(split_demographics[[level]]$GENDER[split_demographics[[level]]$GENDER==2])
  split_means_demo$male[level] <- length(split_demographics[[level]]$GENDER[split_demographics[[level]]$GENDER==1])
  split_means_demo$age[level] <- mean(split_demographics[[level]]$AGE,na.rm=TRUE)
  split_means_demo$age_se[level] <- sd(split_demographics[[level]]$AGE,na.rm=TRUE)/sqrt(length(split_demographics[[level]]$AGE[!is.na(split_demographics[[level]]$AGE)]))
  
}

split_means_demo$level <- as.factor(c("high", "med","low"))
means_melt_demo <- melt(split_means_demo,id.vars="level")


```

```{r create data for demo bar plots, echo=FALSE,warning=FALSE,message=FALSE}

demo_plot_data <- data.frame(level=factor(c("high","med","low","high","med","low"),levels=c("high","med","low")),gender_count=append(split_means_demo$male,split_means_demo$female), scanner_count=append(split_means_demo$Trio,split_means_demo$Prisma),scanner=as.factor(c("Trio","Trio","Trio","Prisma","Prisma","Prisma")),gender=as.factor(c("Male","Male","Male","Female","Female","Female")),care=as.factor(c("CS","CS","CS","NCS","NCS","NCS")),care_count=append(split_means_demo$CS,split_means_demo$NCS))

demo_plot_data.m <- melt(demo_plot_data)

```

# Demographics

```{r plot demographics}

age_plot <- ggplot(data=split_means_demo,aes(x=level,y=age))+
  geom_bar(stat="identity",width = .5, color = "#667Ea4", fill = "#667Ea4")+
  geom_errorbar(aes(ymin=age-age_se,ymax=age+age_se),width=.2)+
  ggtitle("Age") +
  ylab("Mean +/- SE") +
  scale_x_discrete(limits = c("low","med","high")) +
  theme(aspect.ratio = 1)

scanner_data <- demo_plot_data.m[demo_plot_data.m$variable=="scanner_count",c(1,2,5,6)]
scanner_data$value <- scanner_data$value/56*100
scanner_plot <- ggplot(scanner_data,aes(x=level,y=value,fill=scanner))+
  geom_bar(stat="identity") +
  ylab("Percent (%)") +
  theme(aspect.ratio=1) +
  scale_x_discrete(limits = c("low","med","high")) +
  ggtitle("Scanner")

gender_data <- demo_plot_data.m[demo_plot_data.m$variable=="gender_count",c(1,3,5,6)]
gender_data$value <- gender_data$value/56*100
gender_plot <- ggplot(gender_data,aes(x=level,y=value, fill=gender))+
  geom_bar(stat="identity") +
  ylab("Percent (%)") +
  theme(aspect.ratio=1) +
  scale_x_discrete(limits = c("low","med","high")) +
  ggtitle("Gender")


care_data <- demo_plot_data.m[demo_plot_data.m$variable=="care_count",c(1,4:6)]
care_data$value <- care_data$value/56*100
care_plot <- ggplot(care_data,aes(x=level,y=value, fill=care))+
  geom_bar(stat="identity") +
  ylab("Percent (%)") +
  theme(aspect.ratio=1) +
  scale_x_discrete(limits = c("low","med","high")) +
  ggtitle("CS vs NCS")

(age_plot + gender_plot)/(care_plot + scanner_plot)+
  plot_annotation(title="Demographics split by DFR performance")


```


```{r prep fMRI split data for bar plots}

melt_constructs <- prep_split_for_bar_plots(extreme_groups)
melt_clinical <- prep_split_for_bar_plots(split_clinical)
melt_DFR_delay <- prep_split_for_bar_plots(split_DFR_delay)
melt_DFR_cue <- prep_split_for_bar_plots(split_DFR_cue)
melt_DFR_probe <- prep_split_for_bar_plots(split_DFR_probe)
melt_DFR_FFA <- prep_split_for_bar_plots(split_DFR_FFA)
melt_DFR_HPC_Ant <- prep_split_for_bar_plots(split_DFR_HPC_Ant)
melt_DFR_HPC_Med <- prep_split_for_bar_plots(split_DFR_HPC_Med)
melt_DFR_HPC_Post <- prep_split_for_bar_plots(split_DFR_HPC_Post)
melt_fullMask_delay <- prep_split_for_bar_plots(split_fullMask_delay)
melt_cue_ROIs <- prep_split_for_bar_plots(split_cue_ROIs)
melt_cortical_thickness_DFR <- prep_split_for_bar_plots(split_cortical_thickness_DFR)
melt_RS <- prep_split_for_bar_plots(split_RS)
melt_beta_conn_cue <- prep_split_for_bar_plots(split_beta_conn_cue)
melt_beta_conn_delay <- prep_split_for_bar_plots(split_beta_conn_delay)
melt_BCT <- prep_split_for_bar_plots(split_BCT)
melt_indiv_partic_coeff <- prep_split_for_bar_plots(split_indiv_partic_coeff)

```

```{r make ggplots}

constructs_plots <- plot_bars(melt_constructs)
clinical_plots <- plot_bars(melt_clinical)
DFR_delay_plots <- plot_bars(melt_DFR_delay)
DFR_cue_plots <- plot_bars(melt_DFR_cue)
DFR_probe_plots <- plot_bars(melt_DFR_probe)
DFR_FFA_plots <- plot_bars(melt_DFR_FFA)
DFR_HPC_Ant_plots <- plot_bars(melt_DFR_HPC_Ant)
DFR_HPC_Med_plots <- plot_bars(melt_DFR_HPC_Med)
DFR_HPC_Post_plots <- plot_bars(melt_DFR_HPC_Post)
fullMask_delay_plots <- plot_bars(melt_fullMask_delay)
cue_ROIs_plots <- plot_bars(melt_cue_ROIs)
cortical_thickness_plots <- plot_bars(melt_cortical_thickness_DFR)
RS_plots <- plot_bars(melt_RS)
beta_conn_cue_plots <- plot_bars(melt_beta_conn_cue)
beta_conn_delay_plots <- plot_bars(melt_beta_conn_delay)
BCT_plots <- plot_bars(melt_BCT)
indiv_partic_coeff_plots <- plot_bars(melt_indiv_partic_coeff)

```

# Constructs

A nice sanity check here as well - if a subject has higher capacity and higher intelligence, they tend to have higher performance. The main statistically significant differences here are in omnibus span, where high > low. 

```{r plot constructs figures}

constructs_plots[["omnibus_span_no_DFR_MRI"]]$labels$title = "Omnibus Span"

(constructs_plots[["omnibus_span_no_DFR_MRI"]]+constructs_plots[["intelligence"]]+constructs_plots[["LTM"]]) +
  plot_annotation(title="Constructs split on DFR performance")

```

```{r one way ANOVAs for constructs}

print("Omnibus Span")
span.aov <- aov(omnibus_span_no_DFR_MRI ~ level, data=split_constructs[["all"]])
summary(span.aov)
TukeyHSD(span.aov)

print("LTM")
LTM.aov <- aov(LTM ~ level, data=split_constructs[["all"]])
summary(LTM.aov)
TukeyHSD(LTM.aov)

print("Intelligence")
intelligence.aov <- aov(intelligence ~ level, data=split_constructs[["all"]])
summary(intelligence.aov)
TukeyHSD(intelligence.aov)


```

# Clinical


```{r plot clinical}

clinical_plots[["WHO_ST_S32"]]$labels$title <- "WHODAS"
clinical_plots[["BPRS"]]$labels$title <- "BPRS"

(clinical_plots[["WHO_ST_S32"]] + clinical_plots[["BPRS_TOT"]])+
  plot_annotation(title="Clinical measures split by DFR performance")

```

```{r clinical sig testing}

print("WHODAS")
WHODAS.aov <- aov(WHO_ST_S32 ~ level, data=split_clinical[["all"]])
summary(WHODAS.aov)

print("BPRS")
BPRS.aov <- aov(BPRS_TOT ~ level, data=split_clinical[["all"]])
summary(BPRS.aov)

```

# Cue Period 

## Full mask

There is a linear relationship between performance and load effect in the cue mask during the delay period. 

```{r full mask cue}

fullMask_delay_plots[["cue_low"]]+fullMask_delay_plots[["cue_high"]]+fullMask_delay_plots[["cue_loadEffect"]]+
  plot_annotation(title="BOLD signal from full delay period mask during cue period")

```

```{r cue full mask sig testing}

print("Load Effect")
cue_LE.aov <- aov(cue_loadEffect ~ level, data=split_fullMask_delay[["all"]])
summary(cue_LE.aov)
TukeyHSD(cue_LE.aov)

```


## Individual ROIs


```{r plot cue period ROIs}

DFR_cue_plots[["L_FEF_low"]] +  DFR_cue_plots[["L_FEF_high"]] + DFR_cue_plots[["L_FEF_loadEffect"]]

DFR_cue_plots[["L_insula_low"]] +  DFR_cue_plots[["L_insula_high"]] + DFR_cue_plots[["L_insula_loadEffect"]]

DFR_cue_plots[["L_IPS_low"]] +  DFR_cue_plots[["L_IPS_high"]] + DFR_cue_plots[["L_IPS_loadEffect"]]

DFR_cue_plots[["L_occipital_low"]] +  DFR_cue_plots[["L_occipital_high"]] + DFR_cue_plots[["L_occipital_loadEffect"]]

DFR_cue_plots[["R_FEF_low"]] +  DFR_cue_plots[["R_FEF_high"]] + DFR_cue_plots[["R_FEF_loadEffect"]]

DFR_cue_plots[["R_insula_low"]] +  DFR_cue_plots[["R_insula_high"]] + DFR_cue_plots[["R_insula_loadEffect"]]

DFR_cue_plots[["R_IPS_low"]] +  DFR_cue_plots[["R_IPS_high"]] + DFR_cue_plots[["R_IPS_loadEffect"]]

DFR_cue_plots[["R_MFG_low"]] +  DFR_cue_plots[["R_MFG_high"]] + DFR_cue_plots[["R_MFG_loadEffect"]]

DFR_cue_plots[["R_preSMA_low"]] +  DFR_cue_plots[["R_preSMA_high"]] + DFR_cue_plots[["R_preSMA_loadEffect"]]

DFR_cue_plots[["R_occipital_low"]] +  DFR_cue_plots[["R_occipital_high"]] + DFR_cue_plots[["R_occipital_loadEffect"]]


```


```{r cue ROIs ANOVA}

print("L FEF")
cue_L_FEF.aov <- aov(L_FEF_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_L_FEF.aov)

print("L insula")
cue_L_insula.aov <- aov(L_insula_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_L_insula.aov)

print("L IPS")
cue_L_IPS.aov <- aov(L_IPS_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_L_IPS.aov)

print("L occipital")
cue_L_occipital.aov <- aov(L_occipital_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_L_occipital.aov)

print("R FEF")
cue_R_FEF.aov <- aov(R_FEF_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_R_FEF.aov)

print("R insula")
cue_R_insula.aov <- aov(R_insula_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_R_insula.aov)

print("R IPS")
cue_R_IPS.aov <- aov(R_IPS_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_R_IPS.aov)

print("R MFG")
cue_R_MFG.aov <- aov(R_MFG_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_R_MFG.aov)

print("R occipital")
cue_R_occipital.aov <- aov(R_occipital_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_R_occipital.aov)

print("R preSMA")
cue_R_preSMA.aov <- aov(R_preSMA_loadEffect ~ level, data=split_DFR_cue[["all"]])
summary(cue_R_preSMA.aov)

```

# Delay Period

## Full Mask

There are significant differnces in the high load and load effect - the high load trials have differences: high > low and high > medium, while the load effect only has high > low. 

```{r plot full mask delay}

fullMask_delay_plots[["delay_low"]]+fullMask_delay_plots[["delay_high"]]+fullMask_delay_plots[["delay_loadEffect"]]+
  plot_annotation(title="BOLD signal from full delay period mask during delay period")

```

```{r delay full mask sig testing}

print("Low Load")
delay_L1.aov <- aov(delay_low ~ level, data=split_fullMask_delay[["all"]])
summary(delay_L1.aov)

print("High Load")
delay_L3.aov <- aov(delay_high ~ level, data=split_fullMask_delay[["all"]])
summary(delay_L3.aov)

print("Load Effect")
delay_LE.aov <- aov(delay_loadEffect ~ level, data=split_fullMask_delay[["all"]])
summary(delay_LE.aov)

```

## Individual ROIs

No L dMFG, all show high > low, except for . L aMFG, L dlPFC, R dlPFC also showed high > med, and R medial parietal only showed high > med.  

```{r plot delay period DFR ROIs}

(DFR_delay_plots[["DFR_L_aMFG"]] + DFR_delay_plots[["DFR_L_dlPFC"]] + DFR_delay_plots[["DFR_L_dMFG"]]) + plot_annotation(title="individual DFR delay period ROIs")
(DFR_delay_plots[["DFR_L_IPS"]] + DFR_delay_plots[["DFR_L_preSMA"]] + DFR_delay_plots[["DFR_R_dlPFC"]])  
(DFR_delay_plots[["DFR_R_dMFG"]] + DFR_delay_plots[["DFR_R_IPS"]] + DFR_delay_plots[["DFR_R_medParietal"]]) 

```

```{r sig test individual ROIs}

print("L aMFG")
L_aMFG.aov <- aov(DFR_L_aMFG ~ level, data=split_DFR_delay[["all"]])
summary(L_aMFG.aov)
TukeyHSD(L_aMFG.aov)

print("L dlPFC")
L_dlPFC.aov <- aov(DFR_L_dlPFC ~ level, data=split_DFR_delay[["all"]])
summary(L_dlPFC.aov)

print("L dMFG")
L_dMFG.aov <- aov(DFR_L_dMFG ~ level, data=split_DFR_delay[["all"]])
summary(L_dMFG.aov)

print("L IPS")
L_IPS.aov <- aov(DFR_L_IPS ~ level, data=split_DFR_delay[["all"]])
summary(L_IPS.aov)
TukeyHSD(L_IPS.aov)

print("L preSMA")
L_preSMA.aov <- aov(DFR_L_preSMA ~ level, data=split_DFR_delay[["all"]])
summary(L_preSMA.aov)
TukeyHSD(L_preSMA.aov)

print("R dlPFC")
R_dlPFC.aov <- aov(DFR_R_dlPFC ~ level, data=split_DFR_delay[["all"]])
summary(R_dlPFC.aov)

print("R dMFG")
R_dMFG.aov <- aov(DFR_R_dMFG ~ level, data=split_DFR_delay[["all"]])
summary(R_dMFG.aov)

print("R IPS")
R_IPS.aov <- aov(DFR_R_IPS ~ level, data=split_DFR_delay[["all"]])
summary(R_IPS.aov)

print("R medial Parietal")
R_medParietal.aov <- aov(DFR_R_medParietal ~ level, data=split_DFR_delay[["all"]])
summary(R_medParietal.aov)

```

# Probe Period

## Full Mask

No differences in the probe period. 

```{r plot probe full mask}

fullMask_delay_plots[["probe_low"]]+fullMask_delay_plots[["probe_high"]]+fullMask_delay_plots[["probe_loadEffect"]]+
  plot_annotation(title="BOLD signal from full delay period mask during probe period")

```

```{r probe full mask sig testing}

print("Low Load")
probe_L1.aov <- aov(probe_low ~ level, data=split_fullMask_delay[["all"]])
summary(probe_L1.aov)

print("High Load")
probe_L3.aov <- aov(probe_high ~ level, data=split_fullMask_delay[["all"]])
summary(probe_L3.aov)

print("Load Effect")
probe_LE.aov <- aov(probe_loadEffect ~ level, data=split_fullMask_delay[["all"]])
summary(probe_LE.aov)

```

## Individual ROIs

```{r plot probe period ROIs}

DFR_probe_plots[["dmPFC_loadEffect"]] + DFR_probe_plots[["L_aMFG_loadEffect"]] + DFR_probe_plots[["L_dlPFC_loadEffect"]] +
  plot_annotation(title="individual DFR activity from probe period regions")

DFR_probe_plots[["L_insula_loadEffect"]] + DFR_probe_plots[["L_IPS_loadEffect"]] + DFR_probe_plots[["R_dlPFC_loadEffect"]] 

DFR_probe_plots[["R_insula_loadEffect"]] + DFR_probe_plots[["R_OFC_loadEffect"]] 

```

```{r probe ROIs ANOVA}

print("dmPFC")
probe_dmPFC.aov <- aov(dmPFC_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_dmPFC.aov)

print("L aMFG")
probe_L_aMFG.aov <- aov(L_aMFG_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_L_aMFG.aov)

print("L dlPFC")
probe_L_dlPFC.aov <- aov(L_dlPFC_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_L_dlPFC.aov)

print("L insula")
probe_L_insula.aov <- aov(L_insula_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_L_insula.aov)

print("R dlPFC")
probe_R_dlPFC.aov <- aov(R_dlPFC_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_R_dlPFC.aov)

print("R Insula")
probe_R_insula.aov <- aov(R_insula_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_R_insula.aov)

print("R OFC")
probe_R_OFC.aov <- aov(R_OFC_loadEffect ~ level, data=split_DFR_probe[["all"]])
summary(probe_R_OFC.aov)

```

# FFA

No differences. 

```{r plot DFR FFA}

DFR_FFA_plots[["L_CUE_LE"]] + DFR_FFA_plots[["L_DELAY_LE"]] + DFR_FFA_plots[["L_PROBE_LE"]]+
  plot_annotation(title="FFA during DFR task")

DFR_FFA_plots[["R_CUE_LE"]] + DFR_FFA_plots[["R_DELAY_LE"]] + DFR_FFA_plots[["R_PROBE_LE"]]


```

```{r FFA ANOVA}

print("L Cue")
L_CUE_LE_FFA.aov <- aov(L_CUE_LE ~ level, data=split_DFR_FFA[["all"]])
summary(L_CUE_LE_FFA.aov)

print("R Cue")
R_CUE_LE_FFA.aov <- aov(R_CUE_LE ~ level, data=split_DFR_FFA[["all"]])
summary(R_CUE_LE_FFA.aov)

print("L Delay")
L_DELAY_LE_FFA.aov <- aov(L_DELAY_LE ~ level, data=split_DFR_FFA[["all"]])
summary(L_DELAY_LE_FFA.aov)

print("R Delay")
R_DELAY_LE_FFA.aov <- aov(R_DELAY_LE ~ level, data=split_DFR_FFA[["all"]])
summary(R_DELAY_LE_FFA.aov)

print("L Probe")
L_PROBE_LE_FFA.aov <- aov(L_PROBE_LE ~ level, data=split_DFR_FFA[["all"]])
summary(L_PROBE_LE_FFA.aov)

print("R Probe")
R_PROBE_LE_FFA.aov <- aov(R_PROBE_LE ~ level, data=split_DFR_FFA[["all"]])
summary(R_PROBE_LE_FFA.aov)

```

# HPC

Seeing differences in HPC activity in posterior segment for cue and probe L3. 

## Anterior

### L3 

```{r plot HPC L3 Ant}

DFR_HPC_Ant_plots[["L_CUE_L3"]] + DFR_HPC_Ant_plots[["L_DELAY_L3"]] + DFR_HPC_Ant_plots[["L_PROBE_L3"]]+
  plot_annotation(title="HPC Ant during DFR task")

DFR_HPC_Ant_plots[["R_CUE_L3"]] + DFR_HPC_Ant_plots[["R_DELAY_L3"]] + DFR_HPC_Ant_plots[["R_PROBE_L3"]]

```

```{r HPC_Ant L3 ANOVA}

print("L Cue")
L_CUE_L3_HPC_Ant.aov <- aov(L_CUE_L3 ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(L_CUE_L3_HPC_Ant.aov)

print("R Cue")
R_CUE_L3_HPC_Ant.aov <- aov(R_CUE_L3 ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(R_CUE_L3_HPC_Ant.aov)

print("L Delay")
L_DELAY_L3_HPC_Ant.aov <- aov(L_DELAY_L3 ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(L_DELAY_L3_HPC_Ant.aov)

print("R Delay")
R_DELAY_L3_HPC_Ant.aov <- aov(R_DELAY_L3 ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(R_DELAY_L3_HPC_Ant.aov)

print("L Probe")
L_PROBE_L3_HPC_Ant.aov <- aov(L_PROBE_L3 ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(L_PROBE_L3_HPC_Ant.aov)

print("R Probe")
R_PROBE_L3_HPC_Ant.aov <- aov(R_PROBE_L3 ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(R_PROBE_L3_HPC_Ant.aov)

```

### LE 

```{r plot HPC LE Ant}

DFR_HPC_Ant_plots[["L_CUE_LE"]] + DFR_HPC_Ant_plots[["L_DELAY_LE"]] + DFR_HPC_Ant_plots[["L_PROBE_LE"]]+
  plot_annotation(title="HPC Ant during DFR task")

DFR_HPC_Ant_plots[["R_CUE_LE"]] + DFR_HPC_Ant_plots[["R_DELAY_LE"]] + DFR_HPC_Ant_plots[["R_PROBE_LE"]]

```

```{r HPC_Ant LE ANOVA}

print("L Cue")
L_CUE_LE_HPC_Ant.aov <- aov(L_CUE_LE ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(L_CUE_LE_HPC_Ant.aov)

print("R Cue")
R_CUE_LE_HPC_Ant.aov <- aov(R_CUE_LE ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(R_CUE_LE_HPC_Ant.aov)

print("L Delay")
L_DELAY_LE_HPC_Ant.aov <- aov(L_DELAY_LE ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(L_DELAY_LE_HPC_Ant.aov)

print("R Delay")
R_DELAY_LE_HPC_Ant.aov <- aov(R_DELAY_LE ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(R_DELAY_LE_HPC_Ant.aov)

print("L Probe")
L_PROBE_LE_HPC_Ant.aov <- aov(L_PROBE_LE ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(L_PROBE_LE_HPC_Ant.aov)

print("R Probe")
R_PROBE_LE_HPC_Ant.aov <- aov(R_PROBE_LE ~ level, data=split_DFR_HPC_Ant[["all"]])
summary(R_PROBE_LE_HPC_Ant.aov)

```

## Medial

### L3

```{r plot HPC L3 Med}

DFR_HPC_Med_plots[["L_CUE_L3"]] + DFR_HPC_Med_plots[["L_DELAY_L3"]] + DFR_HPC_Med_plots[["L_PROBE_L3"]]+
  plot_annotation(title="HPC_Med during DFR task")

DFR_HPC_Med_plots[["R_CUE_L3"]] + DFR_HPC_Med_plots[["R_DELAY_L3"]] + DFR_HPC_Med_plots[["R_PROBE_L3"]]

```

```{r HPC_Med L3 ANOVA}

print("L Cue")
L_CUE_L3_HPC_Med.aov <- aov(L_CUE_L3 ~ level, data=split_DFR_HPC_Med[["all"]])
summary(L_CUE_L3_HPC_Med.aov)

print("R Cue")
R_CUE_L3_HPC_Med.aov <- aov(R_CUE_L3 ~ level, data=split_DFR_HPC_Med[["all"]])
summary(R_CUE_L3_HPC_Med.aov)

print("L Delay")
L_DELAY_L3_HPC_Med.aov <- aov(L_DELAY_L3 ~ level, data=split_DFR_HPC_Med[["all"]])
summary(L_DELAY_L3_HPC_Med.aov)

print("R Delay")
R_DELAY_L3_HPC_Med.aov <- aov(R_DELAY_L3 ~ level, data=split_DFR_HPC_Med[["all"]])
summary(R_DELAY_L3_HPC_Med.aov)

print("L Probe")
L_PROBE_L3_HPC_Med.aov <- aov(L_PROBE_L3 ~ level, data=split_DFR_HPC_Med[["all"]])
summary(L_PROBE_L3_HPC_Med.aov)

print("R Probe")
R_PROBE_L3_HPC_Med.aov <- aov(R_PROBE_L3 ~ level, data=split_DFR_HPC_Med[["all"]])
summary(R_PROBE_L3_HPC_Med.aov)

```

### LE

```{r plot HPC LE Med}

DFR_HPC_Med_plots[["L_CUE_LE"]] + DFR_HPC_Med_plots[["L_DELAY_LE"]] + DFR_HPC_Med_plots[["L_PROBE_LE"]]+
  plot_annotation(title="HPC_Med during DFR task")

DFR_HPC_Med_plots[["R_CUE_LE"]] + DFR_HPC_Med_plots[["R_DELAY_LE"]] + DFR_HPC_Med_plots[["R_PROBE_LE"]]

```

```{r HPC_Med LE ANOVA}

print("L Cue")
L_CUE_LE_HPC_Med.aov <- aov(L_CUE_LE ~ level, data=split_DFR_HPC_Med[["all"]])
summary(L_CUE_LE_HPC_Med.aov)

print("R Cue")
R_CUE_LE_HPC_Med.aov <- aov(R_CUE_LE ~ level, data=split_DFR_HPC_Med[["all"]])
summary(R_CUE_LE_HPC_Med.aov)

print("L Delay")
L_DELAY_LE_HPC_Med.aov <- aov(L_DELAY_LE ~ level, data=split_DFR_HPC_Med[["all"]])
summary(L_DELAY_LE_HPC_Med.aov)

print("R Delay")
R_DELAY_LE_HPC_Med.aov <- aov(R_DELAY_LE ~ level, data=split_DFR_HPC_Med[["all"]])
summary(R_DELAY_LE_HPC_Med.aov)

print("L Probe")
L_PROBE_LE_HPC_Med.aov <- aov(L_PROBE_LE ~ level, data=split_DFR_HPC_Med[["all"]])
summary(L_PROBE_LE_HPC_Med.aov)

print("R Probe")
R_PROBE_LE_HPC_Med.aov <- aov(R_PROBE_LE ~ level, data=split_DFR_HPC_Med[["all"]])
summary(R_PROBE_LE_HPC_Med.aov)

```

## Posterior

### L3

```{r plot HPC L3 Post}

DFR_HPC_Post_plots[["L_CUE_L3"]] + DFR_HPC_Post_plots[["L_DELAY_L3"]] + DFR_HPC_Post_plots[["L_PROBE_L3"]]+
  plot_annotation(title="HPC_Post during DFR task")

DFR_HPC_Post_plots[["R_CUE_L3"]] + DFR_HPC_Post_plots[["R_DELAY_L3"]] + DFR_HPC_Post_plots[["R_PROBE_L3"]]

```

```{r HPC_Post L3 ANOVA}

print("L Cue")
L_CUE_L3_HPC_Post.aov <- aov(L_CUE_L3 ~ level, data=split_DFR_HPC_Post[["all"]])
summary(L_CUE_L3_HPC_Post.aov)
TukeyHSD(L_CUE_L3_HPC_Post.aov)

print("R Cue")
R_CUE_L3_HPC_Post.aov <- aov(R_CUE_L3 ~ level, data=split_DFR_HPC_Post[["all"]])
summary(R_CUE_L3_HPC_Post.aov)

print("L Delay")
L_DELAY_L3_HPC_Post.aov <- aov(L_DELAY_L3 ~ level, data=split_DFR_HPC_Post[["all"]])
summary(L_DELAY_L3_HPC_Post.aov)

print("R Delay")
R_DELAY_L3_HPC_Post.aov <- aov(R_DELAY_L3 ~ level, data=split_DFR_HPC_Post[["all"]])
summary(R_DELAY_L3_HPC_Post.aov)

print("L Probe")
L_PROBE_L3_HPC_Post.aov <- aov(L_PROBE_L3 ~ level, data=split_DFR_HPC_Post[["all"]])
summary(L_PROBE_L3_HPC_Post.aov)
TukeyHSD(L_PROBE_L3_HPC_Post.aov)


print("R Probe")
R_PROBE_L3_HPC_Post.aov <- aov(R_PROBE_L3 ~ level, data=split_DFR_HPC_Post[["all"]])
summary(R_PROBE_L3_HPC_Post.aov)
TukeyHSD(R_PROBE_L3_HPC_Post.aov)

```

### LE

```{r plot HPC LE Post}

DFR_HPC_Post_plots[["L_CUE_LE"]] + DFR_HPC_Post_plots[["L_DELAY_LE"]] + DFR_HPC_Post_plots[["L_PROBE_LE"]]+
  plot_annotation(title="HPC_Post during DFR task")

DFR_HPC_Post_plots[["R_CUE_LE"]] + DFR_HPC_Post_plots[["R_DELAY_LE"]] + DFR_HPC_Post_plots[["R_PROBE_LE"]]

```

```{r HPC_Post LE ANOVA}

print("L Cue")
L_CUE_LE_HPC_Post.aov <- aov(L_CUE_LE ~ level, data=split_DFR_HPC_Post[["all"]])
summary(L_CUE_LE_HPC_Post.aov)

print("R Cue")
R_CUE_LE_HPC_Post.aov <- aov(R_CUE_LE ~ level, data=split_DFR_HPC_Post[["all"]])
summary(R_CUE_LE_HPC_Post.aov)

print("L Delay")
L_DELAY_LE_HPC_Post.aov <- aov(L_DELAY_LE ~ level, data=split_DFR_HPC_Post[["all"]])
summary(L_DELAY_LE_HPC_Post.aov)

print("R Delay")
R_DELAY_LE_HPC_Post.aov <- aov(R_DELAY_LE ~ level, data=split_DFR_HPC_Post[["all"]])
summary(R_DELAY_LE_HPC_Post.aov)

print("L Probe")
L_PROBE_LE_HPC_Post.aov <- aov(L_PROBE_LE ~ level, data=split_DFR_HPC_Post[["all"]])
summary(L_PROBE_LE_HPC_Post.aov)

print("R Probe")
R_PROBE_LE_HPC_Post.aov <- aov(R_PROBE_LE ~ level, data=split_DFR_HPC_Post[["all"]])
summary(R_PROBE_LE_HPC_Post.aov)

```

# Cortical Thickness 

Only see differences in the L probe regions, with med > high. 

```{r plot cortical thickness splits}

cortical_thickness_plots[["Cue_RH"]] + cortical_thickness_plots[["Delay_RH"]] + cortical_thickness_plots[["Probe_RH"]] + 
  plot_annotation(title="Cortical Thickness from DFR Full Mask") 

cortical_thickness_plots[["Cue_LH"]] + cortical_thickness_plots[["Delay_LH"]] + cortical_thickness_plots[["Probe_LH"]]

```

```{r cortical thickness ANOVA}

print("L Cue")
L_CUE_DFR_thick.aov <- aov(Cue_LH ~ level, data=split_cortical_thickness_DFR[["all"]])
summary(L_CUE_DFR_thick.aov)

print("R Cue")
R_CUE_DFR_thick.aov <- aov(Cue_RH ~ level, data=split_cortical_thickness_DFR[["all"]])
summary(R_CUE_LE_HPC_Post.aov)

print("L Delay")
L_DELAY_DFR_thick.aov <- aov(Delay_LH ~ level, data=split_cortical_thickness_DFR[["all"]])
summary(L_DELAY_DFR_thick.aov)

print("R Delay")
R_DELAY_DFR_thick.aov <- aov(Delay_RH ~ level, data=split_cortical_thickness_DFR[["all"]])
summary(R_DELAY_DFR_thick.aov)

print("L Probe")
L_PROBE_DFR_thick.aov <- aov(Probe_LH ~ level, data=split_cortical_thickness_DFR[["all"]])
summary(L_PROBE_DFR_thick.aov)

print("R Probe")
R_PROBE_DFR_thick.aov <- aov(Probe_RH ~ level, data=split_cortical_thickness_DFR[["all"]])
summary(R_PROBE_DFR_thick.aov)

```

# Resting State Functional Connectivity 

## Within Network 

No differences. 

```{r plot within network RS}

RS_plots[["FPCN_FPCN"]] + RS_plots[["DMN_DMN"]] + RS_plots[["DAN_DAN"]]+
  plot_annotation(title="Resting State Functional Connectivity - Within Networks")
RS_plots[["VAN_VAN"]] + RS_plots[["CO_CO"]] + RS_plots[["visual_visual"]]

```

```{r sig testing within network RS}

print("FPCN")
FPCN.aov <- aov(FPCN_FPCN ~ level, data=split_RS[["all"]])
summary(FPCN.aov)

print("DMN")
DMN.aov <- aov(DMN_DMN ~ level, data=split_RS[["all"]])
summary(DMN.aov)

print("DAN")
DAN.aov <- aov(DAN_DAN ~ level, data=split_RS[["all"]])
summary(DAN.aov)

print("VAN")
VAN.aov <- aov(VAN_VAN ~ level, data=split_RS[["all"]])
summary(VAN.aov)

print("CO")
CO.aov <- aov(CO_CO ~ level, data=split_RS[["all"]])
summary(CO.aov)

print("CO")
visual.aov <- aov(visual_visual ~ level, data=split_RS[["all"]])
summary(visual.aov)

```

## Across Network 

No across RS network differences. 

```{r plot across network RS}

RS_plots[["FPCN_DMN"]] + RS_plots[["FPCN_DAN"]] + RS_plots[["FCPN_VAN"]]+
  plot_annotation(title="Resting State Functional Connectivity - Across Networks")
RS_plots[["FPCN_CO"]] + RS_plots[["FPCN_visual"]]


```

```{r sig testing across network RS}

print("FPCN DMN")
FPCN_DMN.aov <- aov(FPCN_DMN ~ level, data=split_RS[["all"]])
summary(FPCN_DMN.aov)

print("FPCN DAN")
FPCN_DAN.aov <- aov(FPCN_DAN ~ level, data=split_RS[["all"]])
summary(FPCN_DAN.aov)

print("FPCN VAN")
FPCN_VAN.aov <- aov(FPCN_VAN ~ level, data=split_RS[["all"]])
summary(FPCN_VAN.aov)

print("FPCN CO")
FPCN_CO.aov <- aov(FPCN_CO ~ level, data=split_RS[["all"]])
summary(FPCN_CO.aov)

print("FPCN visual")
FPCN_visual.aov <- aov(FPCN_visual ~ level, data=split_RS[["all"]])
summary(FPCN_visual.aov)

```

# Beta Series Connectivity 

## Cue Period 

### High Load

No differences. 

```{r beta conn cue L3} 

beta_conn_cue_plots[["FPCN_FPCN_L3"]] + beta_conn_cue_plots[["FPCN_HPC_L3"]] +
  plot_annotation(title = "Beta Series Connectivity at High Load")
beta_conn_cue_plots[["FPCN_FFA_L3"]] + beta_conn_cue_plots[["HPC_FFA_L3"]]

```

```{r sig test beta conn cue L3}

FPCN_FPCN_BC_cue_L3.aov <- aov(FPCN_FPCN_L3 ~ level, data = split_beta_conn_cue[["all"]])
summary(FPCN_FPCN_BC_cue_L3.aov)

FPCN_HPC_BC_cue_L3.aov <- aov(FPCN_HPC_L3 ~ level, data = split_beta_conn_cue[["all"]])
summary(FPCN_HPC_BC_cue_L3.aov)

FPCN_FFA_BC_cue_L3.aov <- aov(FPCN_FFA_L3 ~ level, data = split_beta_conn_cue[["all"]])
summary(FPCN_FFA_BC_cue_L3.aov)

HPC_FFA_BC_cue_L3.aov <- aov(HPC_FFA_L3 ~ level, data = split_beta_conn_cue[["all"]])
summary(HPC_FFA_BC_cue_L3.aov)

```

### Load Effect 

No differences. 

```{r beta conn cue LE} 

beta_conn_cue_plots[["FPCN_FPCN_LE"]] + beta_conn_cue_plots[["FPCN_HPC_LE"]] +
  plot_annotation(title = "Beta Series Connectivity Load Effect")
beta_conn_cue_plots[["FPCN_FFA_LE"]] + beta_conn_cue_plots[["HPC_FFA_LE"]]

```

```{r sig testing beta conn cue LE}

FPCN_FPCN_BC_cue_LE.aov <- aov(FPCN_FPCN_LE ~ level, data = split_beta_conn_cue[["all"]])
summary(FPCN_FPCN_BC_cue_LE.aov)

FPCN_HPC_BC_cue_LE.aov <- aov(FPCN_HPC_LE ~ level, data = split_beta_conn_cue[["all"]])
summary(FPCN_HPC_BC_cue_LE.aov)

FPCN_FFA_BC_cue_LE.aov <- aov(FPCN_FFA_LE ~ level, data = split_beta_conn_cue[["all"]])
summary(FPCN_FFA_BC_cue_LE.aov)

HPC_FFA_BC_cue_LE.aov <- aov(HPC_FFA_LE ~ level, data = split_beta_conn_cue[["all"]])
summary(HPC_FFA_BC_cue_LE.aov)


```


## Delay Period 

No differences for the beta series connectivity during delay period. 

### High Load

```{r beta conn delay L3} 

beta_conn_delay_plots[["FPCN_FPCN_L3"]] + beta_conn_delay_plots[["FPCN_HPC_L3"]] +
  plot_annotation(title = "Beta Series Connectivity at High Load")
beta_conn_delay_plots[["FPCN_FFA_L3"]] + beta_conn_delay_plots[["HPC_FFA_L3"]]

```

```{r sig testing beta conn L3}

FPCN_FPCN_BC_delay_L3.aov <- aov(FPCN_FPCN_L3 ~ level, data = split_beta_conn_delay[["all"]])
summary(FPCN_FPCN_BC_delay_L3.aov)

FPCN_HPC_BC_delay_L3.aov <- aov(FPCN_HPC_L3 ~ level, data = split_beta_conn_delay[["all"]])
summary(FPCN_HPC_BC_delay_L3.aov)

FPCN_FFA_BC_delay_L3.aov <- aov(FPCN_FFA_L3 ~ level, data = split_beta_conn_delay[["all"]])
summary(FPCN_FFA_BC_delay_L3.aov)

HPC_FFA_BC_delay_L3.aov <- aov(HPC_FFA_L3 ~ level, data = split_beta_conn_delay[["all"]])
summary(HPC_FFA_BC_delay_L3.aov)

```

### Load Effect 

Differences between the HPC/FFA connectivity - low > med. 

```{r beta conn delay LE} 

beta_conn_delay_plots[["FPCN_FPCN_LE"]] + beta_conn_delay_plots[["FPCN_HPC_LE"]] +
  plot_annotation(title = "Beta Series Connectivity Load Effect")
beta_conn_delay_plots[["FPCN_FFA_LE"]] + beta_conn_delay_plots[["HPC_FFA_LE"]]

```

```{r sig testing beta conn delay LE}

FPCN_FPCN_BC_delay_LE.aov <- aov(FPCN_FPCN_LE ~ level, data = split_beta_conn_delay[["all"]])
summary(FPCN_FPCN_BC_delay_LE.aov)

FPCN_HPC_BC_delay_LE.aov <- aov(FPCN_HPC_LE ~ level, data = split_beta_conn_delay[["all"]])
summary(FPCN_HPC_BC_delay_LE.aov)

FPCN_FFA_BC_delay_LE.aov <- aov(FPCN_FFA_LE ~ level, data = split_beta_conn_delay[["all"]])
summary(FPCN_FFA_BC_delay_LE.aov)

HPC_FFA_BC_delay_LE.aov <- aov(HPC_FFA_LE ~ level, data = split_beta_conn_delay[["all"]])
summary(HPC_FFA_BC_delay_LE.aov)
TukeyHSD(HPC_FFA_BC_delay_LE.aov)

```

# BCT Measures 

No differences in any of the BCT measures. 

## Overall Measures 

```{r plot BCT measures}

BCT_plots[["Participation_Coef_Mean"]] + BCT_plots[["Global_Eff"]] + BCT_plots[["Modularity_Louvain_N"]]+
  plot_annotation(title="Overall BCT Measures")

```

```{r sig testing overall BCT measures}
print("Mean Participation Coefficient")
partic_coef_mean.aov <- aov(Participation_Coef_Mean ~ level, data = split_BCT[["all"]])
summary(partic_coef_mean.aov)

print("Global Efficiency")
global_eff.aov <- aov(Global_Eff ~ level, data = split_BCT[["all"]])
summary(global_eff.aov)

print("Modularity")
modularity.aov <- aov(Modularity_Louvain_N ~ level, data = split_BCT[["all"]])
summary(modularity.aov)

```

## Individual Networks 

```{r plot individual network participation coefficients}

indiv_partic_coeff_plots[["FrontoParietal"]] + indiv_partic_coeff_plots[["Default"]] + indiv_partic_coeff_plots[["DorsalAttn"]]+
  plot_annotation(title="Individual Network Participation Coefficient")
indiv_partic_coeff_plots[["CinguloOperc"]] + indiv_partic_coeff_plots[["VentralAttn"]] + indiv_partic_coeff_plots[["Visual"]]

```

```{r sig test indiv partic coeff}

print("FPCN")
FPCN_indiv_coeff.aov <- aov(FrontoParietal ~ level, data = split_indiv_partic_coeff[["all"]])
summary(FPCN_indiv_coeff.aov)

print("DMN")
DMN_indiv_coeff.aov <- aov(Default ~ level, data = split_indiv_partic_coeff[["all"]])
summary(DMN_indiv_coeff.aov)

print("DAN")
DAN_indiv_coeff.aov <- aov(DorsalAttn ~ level, data = split_indiv_partic_coeff[["all"]])
summary(DAN_indiv_coeff.aov)

print("CO")
CO_indiv_coeff.aov <- aov(CinguloOperc ~ level, data = split_indiv_partic_coeff[["all"]])
summary(CO_indiv_coeff.aov)

print("VAN")
VAN_indiv_coeff.aov <- aov(VentralAttn ~ level, data = split_indiv_partic_coeff[["all"]])
summary(VAN_indiv_coeff.aov)

print("visual")
visual_indiv_coeff.aov <- aov(Visual ~ level, data = split_indiv_partic_coeff[["all"]])
summary(visual_indiv_coeff.aov)


```

