---
title: "SEM Final"
author: "Catherine Walsh"
date: "12/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load libraries}

library(tidyverse)
library(lavaan)
library(semPlot)
library(readxl)
library(MVN)
library(nonnest2)
library(knitr)

```

```{r}

pIDs_pop200 <- read_excel("~/Documents/UCLA/Research/RDoC/pop200.xls", col_names = FALSE)
behav <- read.csv("~/Documents/UCLA/Research/RDoC/RDoC_CATHERINE_QUERY5.csv")

behav <- behav[behav$PTID %in% pIDs_pop200$...1,c(1,10, 12:13, 23:24,36:38, 41, 44,51, 53, 55, 57, 59:62)]

all_behav <- read_excel("~/Documents/UCLA/Research/RDoC/RDoC_Merged_Behavior_pop200.xlsx")
filling_in <- dplyr::select(all_behav,Xsub,XAOS_part_score,XLCD_K_MAX,XDPX_DPRIME,XDFR_MRI_acc_L1,XDFR_MRI_acc_L3,XNR_Lure_vs_Control_ErrorRate, XRISE_Pr_item,XRISE_Pr_relat,Xscap_max_capac,XSCWT_CONFLICT_RT_EFFECT)
colnames(filling_in) <- colnames(behav)[1:11]
behav[,1:11] <- filling_in

# z score 

behav_zscore <- data.frame(scale(behav))
behav_zscore$PTID <- behav$PTID
behav_zscore$load_effect <- behav_zscore$XDFR_MRI_ACC_L3 - behav_zscore$XDFR_MRI_ACC_L1

```

Our data is not multivariate normal. 

```{r check data for normality}

mvn(behav_zscore[,c(2:4,7:20)], mvnTest = "mardia", univariatePlot = "histogram")

```


```{r calculate covariance matrix}

cov_matrix <- cov(behav_zscore[,2:20], use = "pairwise.complete.obs")
#View(cor(behav_zscore[,2:20], use = "pairwise.complete.obs"))

colnames(cov_matrix) <-c("AOS", "LCD", "DPX", "DFR L1", "DFR L3", "RN", "RISE - Item", "RISE - Relat",
                         "SCAP", "Stroop", "LNS", "DS - Fwd", "DS - Back", "DS - Seq", "Mat Reas", 
                         "Vocab", "SA","SS", "Load Effect")

rownames(cov_matrix) <-c("AOS", "LCD", "DPX", "DFR L1", "DFR L3", "RN", "RISE - Item", "RISE - Relat",
                         "SCAP", "Stroop", "LNS", "DS - Fwd", "DS - Back", "DS - Seq", "Mat Reas", 
                         "Vocab", "SA","SS", "Load Effect")



```

First model does not fit great - if we look at residuals, clearly we need to add in some correlations, particularly between desk tests and neuropsych tests, which are of the same format. 

```{r simple vs complex - predicting DFR score no corrs}

model1 <- '
  #measurement model 
    intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  GM_IC =~ XAOS_PART_SCORE + XDPX_DPRIME + XNR_LURE_VS_CONTROL_ERRORRATE
  simple_span =~ XSCAP_MAX_CAPAC + XLCD_K_MAX+ WMS_SYMS_TOTSCORE + ANALYSIS_DIGITSPANFWD_RAW  
  complex_span =~ SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + WMS_SA_TOTSCORE 
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM

  load_effect ~ simple_span + complex_span + GM_IC + LTM + intelligence


'
simple_complex_labs <- c("Vocab", "MatRea","AOS","DPX", "RN", "SCAP","LCD","Sym\nSpan", "DS\nFwd", "LetNum\nSeq", 
                         "DS\nBkd","DS\nSeq","SA",
                         "RISE\nRelat", "RISE\nItem",  "Load\nEffect", "Intelligence","GM/IC", "Simple\nSpan",
                         "Complex\nSpan","LTM")
fit.model1 <- sem(model1, data = behav_zscore[,2:20], estimator = "WLS")
semPaths(fit.model1,nodeLabels = simple_complex_labs, style="lisrel")


summary(fit.model1,fit.measures=TRUE)
standardizedSolution(fit.model1)

residuals(fit.model1, type = "cor")


```

Adding in these correlations create a much better fit! 

```{r simple vs complex - let things correlate}

model2 <- '
  #measurement model 
  simple_span =~ XSCAP_MAX_CAPAC + XLCD_K_MAX+ WMS_SYMS_TOTSCORE + ANALYSIS_DIGITSPANFWD_RAW  
  complex_span =~ SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + WMS_SA_TOTSCORE + XAOS_PART_SCORE
  GM_IC =~ XAOS_PART_SCORE + XDPX_DPRIME + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  load_effect ~ simple_span + complex_span + GM_IC + LTM + intelligence


'
fit.model2 <- sem(model2, data = behav_zscore[,2:20], estimator = "WLS")
simple_complex_labs <- c("SCAP","LCD","Sym\nSpan", "DS\nFwd", "LetNum\nSeq", "DS\nBkd","DS\nSeq","SA", "AOS", "DPX", "RN", 
                         "RISE\nRelat", "RISE\nItem", "Vocab", "MatRea", "Load Effect", "Simple\nSpan", "Complex\nSpan", 
                         "GM/IC","LTM", "Intelligence")
semPaths(fit.model2)

summary(fit.model2,fit.measures=TRUE)
standardizedSolution(fit.model2)

residuals(fit.model2, type = "cor")



```

Let's add in more correlations to reduce residuals. Looks like there's unexplained variance between LTM and all the simple span tasks, so let's add it in at that level.

```{r simple vs complex 4}

model4 <- '
  #measurement model 
    intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  GM_IC =~ XAOS_PART_SCORE + XDPX_DPRIME + XNR_LURE_VS_CONTROL_ERRORRATE
  simple_span =~ XSCAP_MAX_CAPAC + XLCD_K_MAX+ WMS_SYMS_TOTSCORE + ANALYSIS_DIGITSPANFWD_RAW  
  complex_span =~ SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + WMS_SA_TOTSCORE 
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  LTM ~~ simple_span
  LTM ~~ complex_span
  
  XNR_LURE_VS_CONTROL_ERRORRATE ~~ ANALYSIS_DIGITSPANFWD_RAW 
  XAOS_PART_SCORE ~~ ANALYSIS_DIGITSPANFWD_RAW
  ANALYSIS_DIGITSPANFWD_RAW  ~~ VOCABULARY_TOTALRAWSCORE
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX
  XSCAP_MAX_CAPAC ~~ XDPX_DPRIME
  XSCAP_MAX_CAPAC ~~ MATRIXREASONING_TOTALRAWSCORE
  XNR_LURE_VS_CONTROL_ERRORRATE ~~ XRISE_PR_ITEM
  VOCABULARY_TOTALRAWSCORE ~~ SCORING_LETNUMSEQ_RAW
  
  load_effect ~ simple_span + complex_span + GM_IC + LTM + intelligence


'
fit.model4 <- sem(model4, data = behav_zscore[,2:20], estimator = "WLS")
# simple_complex_labs <- c("Vocab", "MatRea","DPX", "RN", "SCAP","LCD","Sym\nSpan", "DS\nFwd","AOS", "LetNum\nSeq", 
#                          "DS\nBkd","DS\nSeq","SA",
#                          "RISE\nRelat", "RISE\nItem",  "Load\nEffect", "Intelligence","GM/IC", "Simple\nSpan",
#                          "Complex\nSpan","LTM")
semPaths(fit.model4,style="lisrel")
semPaths(fit.model4,style="lisrel", nodeLabels = simple_complex_labs, whatLabels = "std")
summary(fit.model4,fit.measures=TRUE)
standardizedSolution(fit.model4) 

model_fit <- standardizedSolution(fit.model4) 
write.csv(model_fit,"~/Box/UCLA/Class/M257/final/stats.csv")

residuals(fit.model4, type = "cor")

```

```{r}

anova(fit.model1, fit.model4)

```


```{r omnibus span no corrs - predicting DFR score}

model6 <- '
  #measurement model 
  omnibus_span =~ ANALYSIS_DIGITSPANFWD_RAW + WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX+SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + WMS_SA_TOTSCORE
  GM_IC =~ XAOS_PART_SCORE + XDPX_DPRIME + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  load_effect ~ omnibus_span + GM_IC + LTM + intelligence

'
fit.model6 <- sem(model6, data = behav_zscore[,2:20], estimator = "WLS")
sem_labs_omni <- c("DS\nFwd","Sym\nSpan", "SCAP", "LCD","LetNum\nSeq", "DS\nBkd", "DS\nSeq", "SA", "AOS", "DPX",   
              "RN", "RISE\nRelat", "RISE\nItem", "Vocab","MatRea", "Load\nEffect", "Omnibus\nSpan", "GM/IC","LTM", "Intelligence")
semPaths(fit.model6, style="lisrel", nodeLabels = sem_labs_omni)


summary(fit.model6,fit.measures=TRUE)
standardizedSolution(fit.model6)
residuals(fit.model6, type = "cor")


```

```{r omnibus span with corrs - predicting DFR score}

model5 <- '
  #measurement model 
  omnibus_span =~ ANALYSIS_DIGITSPANFWD_RAW + WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX+SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + WMS_SA_TOTSCORE 
  GM_IC =~ XAOS_PART_SCORE + XDPX_DPRIME + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW

  LTM ~~ omnibus_span
  
  XNR_LURE_VS_CONTROL_ERRORRATE ~~ ANALYSIS_DIGITSPANFWD_RAW 
  XAOS_PART_SCORE ~~ ANALYSIS_DIGITSPANFWD_RAW
  ANALYSIS_DIGITSPANFWD_RAW  ~~ VOCABULARY_TOTALRAWSCORE
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX
  XSCAP_MAX_CAPAC ~~ XDPX_DPRIME
  XSCAP_MAX_CAPAC ~~ MATRIXREASONING_TOTALRAWSCORE
  XNR_LURE_VS_CONTROL_ERRORRATE ~~ XRISE_PR_ITEM
  VOCABULARY_TOTALRAWSCORE ~~ SCORING_LETNUMSEQ_RAW

  load_effect ~ omnibus_span + GM_IC + LTM + intelligence

'
fit.model5 <- sem(model5, data = behav_zscore[,2:20], estimator = "WLS")
sem_labs_omni <- c("DS\nFwd","Sym\nSpan", "SCAP", "LCD","LetNum\nSeq", "DS\nBkd", "DS\nSeq", "SA", "AOS", "DPX",   
              "RN", "RISE\nRelat", "RISE\nItem", "Vocab","MatRea", "Load\nEffect", "Omnibus\nSpan", "GM/IC","LTM", "Intelligence")

semPaths(fit.model5, style= "lisrel", nodeLabels = sem_labs_omni)

summary(fit.model5,fit.measures=TRUE)
standardizedSolution(fit.model5)
residuals(fit.model5, type = "cor")


```

```{r}

# model 6 has no correlations, model5 does
anova(fit.model6, fit.model5)

#model 5 = omnibus, model4 = simple/complex
anova(fit.model5, fit.model4)

```




Other option - visual vs verbal separately, with a common WM latent variable. We know that adding in the correlations improves fit, so let's keep those in there. Not significant, but we are getting decent fit indices and RMSEA. 

```{r visual vs verbal no corrs}

model_visual_verbal1 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE
    LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM

  load_effect ~ visual+verbal + LTM + intelligence
  

'
fit.model_visual_verbal1 <- sem(model_visual_verbal1, data = behav_zscore[,2:20], estimator = "WLS")
summary(fit.model_visual_verbal1,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal1)

sem_labs_vis <- c("Sym\nSpan", "SCAP", "LCD", "SA", "DPX", "DS\nFwd", "LetNum\nSeq", "DS\nBkd", "DS\nSeq",
                  "AOS", "RN", "Vocab", "MatRea","RISE\nItem", "RISE\nRelat", "Load\nEffect", "Visual", "Verbal",  "Intelligence","LTM")
semPaths(fit.model_visual_verbal1,style="lisrel", nodeLabels = sem_labs_vis)
semPaths(fit.model_visual_verbal1, style="lisrel")

residuals(fit.model_visual_verbal1, type = "cor")


```


```{r visual vs verbal}

model_visual_verbal1 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  load_effect ~ visual+verbal + LTM + intelligence
  

  # allow tasks to correlate 
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
'
fit.model_visual_verbal1 <- sem(model_visual_verbal1, data = behav_zscore[,2:20], estimator = "MLM")
summary(fit.model_visual_verbal1,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal1)

semPaths(fit.model_visual_verbal1)
residuals(fit.model_visual_verbal1, type = "cor")


```

If we look at residuals, seems like there might be some relationship that we're not accounting for between the verbal WM measures and vocabulary (which is also a verbal task) and visual and matrix reasoning - so let's allow that to correlate. This improves the residuals there.


```{r visual vs verbal 2}

model_visual_verbal2 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  WM =~ visual+verbal
  load_effect ~ WM + LTM + intelligence
  
  verbal ~~ VOCABULARY_TOTALRAWSCORE
  visual ~~ MATRIXREASONING_TOTALRAWSCORE


  LTM ~~ visual
  # allow tasks to correlate 
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW

'
fit.model_visual_verbal2 <- sem(model_visual_verbal2, data = behav_zscore[,2:20], estimator = "MLM")
summary(fit.model_visual_verbal2,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal2)

semPaths(fit.model_visual_verbal2)
residuals(fit.model_visual_verbal2, type = "cor")


```

If we take a look at the residuals again, we see that there seem to be some unaccounted for residuals in the desk tesks - let's let them correlate as well. 


```{r visual vs verbal3}

model_visual_verbal3 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  WM =~ visual+verbal
  load_effect ~ WM + LTM + intelligence
  
  verbal ~~ VOCABULARY_TOTALRAWSCORE
  visual ~~ MATRIXREASONING_TOTALRAWSCORE


  # allow tasks to correlate 
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  XDPX_DPRIME ~~ XSCAP_MAX_CAPAC
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX 

'
fit.model_visual_verbal3 <- sem(model_visual_verbal3, data = behav_zscore[,2:20], estimator = "MLM")
summary(fit.model_visual_verbal3,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal3)

semPaths(fit.model_visual_verbal3)
residuals(fit.model_visual_verbal3, type = "cor")


```

There seems to be a relatively large residual between LCD K max and digits forward, which theoretically measure the same thing, so let's let them correlate

```{r visual vs verbal4}

model_visual_verbal4 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE

  WM =~ visual+verbal
  load_effect ~ WM + LTM + intelligence
  
  verbal ~~ VOCABULARY_TOTALRAWSCORE
  visual ~~ MATRIXREASONING_TOTALRAWSCORE


  # allow tasks to correlate 
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  XDPX_DPRIME ~~ XSCAP_MAX_CAPAC
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX 
  XLCD_K_MAX ~~ ANALYSIS_DIGITSPANFWD_RAW


'
fit.model_visual_verbal4 <- sem(model_visual_verbal4, data = behav_zscore[,2:20], estimator = "MLM")
summary(fit.model_visual_verbal4,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal4)

semPaths(fit.model_visual_verbal4)
residuals(fit.model_visual_verbal4, type = "cor")


```

Also noticing a large residual for symbol span and DPX - let's add that in. 

```{r visual vs verbal5}

model_visual_verbal5 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE
  
  WM =~ visual+verbal
  
  ## regression
  load_effect ~ WM + LTM + intelligence
  
  verbal ~~ VOCABULARY_TOTALRAWSCORE
  visual ~~ MATRIXREASONING_TOTALRAWSCORE

  # allow tasks to correlate 
  
  ## neuropsych tasks
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  ## desk tasks 
  XDPX_DPRIME ~~ XSCAP_MAX_CAPAC  
  XDPX_DPRIME ~~ WMS_SYMS_TOTSCORE
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX 
  
  ## capacity measures 
  XLCD_K_MAX ~~ ANALYSIS_DIGITSPANFWD_RAW


'
fit.model_visual_verbal5 <- sem(model_visual_verbal5, data = behav_zscore[,2:20], estimator = "MLM")
summary(fit.model_visual_verbal5,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal5)

semPaths(fit.model_visual_verbal5)
residuals(fit.model_visual_verbal5, type = "cor")


```

Finally, seeing some large residuals with intelligence and WM measures - let's add in that correlation. 

```{r visual vs verbal9}

model_visual_verbal9 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE
    LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM


  intelligence ~~ visual 
  intelligence ~~ verbal
  
  verbal ~~ VOCABULARY_TOTALRAWSCORE
  visual ~~ MATRIXREASONING_TOTALRAWSCORE

  # regression
  load_effect ~ visual + verbal + LTM + intelligence

  # allow tasks to correlate 
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  XDPX_DPRIME ~~ XSCAP_MAX_CAPAC  
  XDPX_DPRIME ~~ WMS_SYMS_TOTSCORE
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX 
  XLCD_K_MAX ~~ ANALYSIS_DIGITSPANFWD_RAW

'
fit.model_visual_verbal9 <- sem(model_visual_verbal9, data = behav_zscore[,2:20], estimator = "WLS")
summary(fit.model_visual_verbal9,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal9)


sem_labs_vis <- c("Sym\nSpan", "SCAP", "LCD", "SA", "DPX","MatRea", "DS\nFwd", "LetNum\nSeq", "DS\nBkd", "DS\nSeq",
                  "AOS", "RN", "Vocab", "RISE\nItem", "RISE\nRelat", "Load\nEffect", "Visual", "Verbal",  "Intelligence","LTM")
semPaths(fit.model_visual_verbal9, style="lisrel", nodeLabels = sem_labs_vis)
semPaths(fit.model_visual_verbal9, style="lisrel")

residuals(fit.model_visual_verbal9, type = "cor")


```

```{r}
#model 9 includes correlations, model 1 does not
anova(fit.model_visual_verbal9, fit.model_visual_verbal1)

#model 4 is simple/complex
anova(fit.model4, fit.model_visual_verbal9)

```

```{r visual vs verbal10}

model_visual_verbal10 <- '
  #measurement model 
  visual =~ WMS_SYMS_TOTSCORE + XSCAP_MAX_CAPAC + XLCD_K_MAX + WMS_SA_TOTSCORE + XDPX_DPRIME
  verbal =~ ANALYSIS_DIGITSPANFWD_RAW + SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + XAOS_PART_SCORE + XNR_LURE_VS_CONTROL_ERRORRATE 
  intelligence =~ VOCABULARY_TOTALRAWSCORE + MATRIXREASONING_TOTALRAWSCORE
    LTM =~ XRISE_PR_RELAT + XRISE_PR_ITEM

  GM_IC =~ XAOS_PART_SCORE + XDPX_DPRIME + XNR_LURE_VS_CONTROL_ERRORRATE
  simple_span =~ XSCAP_MAX_CAPAC + XLCD_K_MAX+ WMS_SYMS_TOTSCORE + ANALYSIS_DIGITSPANFWD_RAW  
  complex_span =~ SCORING_LETNUMSEQ_RAW + ANALYSIS_DIGITSPANBKW_RAW + ANALYSIS_DIGITSPANSEQ_RAW + WMS_SA_TOTSCORE 

  
 

  # regression
  load_effect ~ simple_span + complex_span + LTM + intelligence

  # allow tasks to correlate 
  ANALYSIS_DIGITSPANFWD_RAW ~~ SCORING_LETNUMSEQ_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  ANALYSIS_DIGITSPANFWD_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANBKW_RAW
  SCORING_LETNUMSEQ_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  ANALYSIS_DIGITSPANBKW_RAW ~~ ANALYSIS_DIGITSPANSEQ_RAW
  
  XDPX_DPRIME ~~ XSCAP_MAX_CAPAC  
  XDPX_DPRIME ~~ WMS_SYMS_TOTSCORE
  XSCAP_MAX_CAPAC ~~ XLCD_K_MAX 
  #XLCD_K_MAX ~~ ANALYSIS_DIGITSPANFWD_RAW

'
fit.model_visual_verbal10 <- sem(model_visual_verbal10, data = behav_zscore[,2:20], estimator = "WLS")
summary(fit.model_visual_verbal10,fit.measures=TRUE)
standardizedSolution(fit.model_visual_verbal10)


#sem_labs_vis <- c("Sym\nSpan", "SCAP", "LCD", "SA", "DPX","MatRea", "DS\nFwd", "LetNum\nSeq", "DS\nBkd", "DS\nSeq",
                  #"AOS", "RN", "Vocab", "RISE\nItem", "RISE\nRelat", "Load\nEffect", "Visual", "Verbal",  "Intelligence","LTM")
#semPaths(fit.model_visual_verbal9, style="lisrel", nodeLabels = sem_labs_vis)
semPaths(fit.model_visual_verbal10, style="lisrel")

# residuals(fit.model_visual_verbal10, type = "cor")


```
